\section{Introduction}
\label{sec:introduction}

Authenticated encryption with associated data is the workhorse of applied
cryptography, and the sponge and duplex constructions over a single public
permutation offer an attractive route to it. The duplex of \cite{BDPV11} turns
one permutation---here \Keccakp, the round-reduced permutation
underlying the \cite{FIPS202} standard---into a single-pass authenticated cipher
with a small, constant memory footprint and no separate block cipher or
universal-hash key schedule. Its security rests on the indifferentiability of
the sponge from a random oracle \cite{BDPV08}, which reduces analysis of the full
construction to a random-oracle argument plus one capacity-birthday loss.

This compactness comes at a structural cost. A duplex is inherently
\emph{sequential}: each call absorbs its input into a state produced by the
previous call, so a single duplex cannot exploit the wide SIMD and multicore
parallelism of modern processors, on which competing designs built from AES
reach many bytes per cycle. A second, orthogonal gap is \emph{commitment}.
Widely deployed AEADs such as AES-GCM and ChaCha20-Poly1305 are not
key-committing: an adversary can craft a single ciphertext that decrypts to
valid plaintexts under two or more keys \cite{DGRW18, ADGKLS22}. Far from a
curiosity, this enables concrete abuses---the ``invisible salamander'' that
defeats Facebook's attachment-franking scheme \cite{DGRW18}, ciphertexts that
open to different well-formed files under different keys \cite{ADGKLS22}, and
partitioning-oracle attacks that recover passwords from systems built on
non-committing AEAD \cite{LGR21}. The committing-AE line that addresses these
threats was initiated by \cite{GLR17} and developed into formal committing
notions with efficient generic transforms by \cite{BH22}. Commitment has two
facets: committing security is a collision requirement---no two contexts open
one ciphertext---while its preimage counterpart, \emph{context discoverability}
\cite{MLGR23}, forbids an adversary from \emph{finding} even one decrypting
context for a target ciphertext. The latter's absence underlies the recent
context-discovery attacks that break \textsf{GCM}, \textsf{CCM}, \textsf{EAX},
\textsf{SIV}, and \textsf{OCB3} \cite{MLGR23}, all of which delegate
authenticity to an algebraically invertible MAC. A mode that targets these
notions natively, rather than through an add-on transform, avoids the
transform's overhead and binds commitment to the same permutation it already
uses for confidentiality and integrity.

\TW{} (\emph{TreeWrap}) addresses both gaps with a two-level tree of keyed
duplexes. A serial
\emph{root} duplex, initialized with the key $K$ and nonce $N$, absorbs the
associated data, encrypts the first message chunk, and absorbs a tag from every
other chunk before emitting the final authentication tag. The remaining chunks
are processed by independent \emph{leaf} duplexes, each keyed by $(K, N, j)$ and
operating on disjoint state and disjoint input. Because the leaves share nothing
once $(K, N)$ is fixed, they can be evaluated in parallel across SIMD lanes,
recovering the throughput a flat duplex forgoes; and because the root binds the
associated data, the first chunk, and every leaf tag into the single output tag,
that tag is the output of the sponge on the entire $(K, N, A, M)$ input. The structure
ensures only that distinct $(K, N, A)$ triples reach distinct root transcripts;
the committing and context-discoverability security rests on the
indifferentiability of the sponge, which makes the root tag both collision- and
preimage-resistant. Because both hold for the tag projection alone, the single
$256$-bit root tag is itself a secure, compact cryptographic commitment to the
full $(K, N, A, M)$ context (\Cref{sec:cmtds3}). Every duplex
still operates on a bounded $1600$-bit state, and the leaf tags are absorbed
into the root as the leaves complete rather than buffered together, so the
memory footprint remains constant in the message length.

We analyze \TW{} in the public-permutation model and obtain concrete bounds for
the standard and tag-committing notions: all-in-one authenticated encryption in the sense of
\cite{RS06}, its multi-user indistinguishability lift in the sense of
\cite{BT16}, and both facets of commitment: the collision facet---$s$-way
committing security in the strongest full-input sense (\textsf{CMTDs-4}) of
\cite{BH22} and its tag-committing compact strengthening---and the preimage
facet, given both as the tag-target \textsf{T-CDY} and as the \cite{MLGR23}
context-discoverability notion. Each bound is proved first against an
intermediate random oracle and then transferred to the real permutation by the
flat-sponge lift of \cite{BDPV08}. At the implemented parameters
($k = c = \tauroot = \tauleaf = 256$), these guarantees meet a $128$-bit
security target for adversaries running up to $\Ntot \leq 2^{63}$ \Keccakp{}
calls---on the order of $2^{71}$ bytes of processed data, beyond any realistic
deployment lifetime. Optimized \texttt{amd64} and \texttt{arm64} implementations
turn the tree's leaf parallelism into measured throughput within a small factor
of hardware-accelerated AES-128-GCM (\Cref{sec:performance}).

\subsection{Our Contributions}
\label{sec:contributions}

\begin{itemize}
\item \textbf{The \TW{} mode.} We specify \TW{}, a nonce-based AEAD with
  associated data built as a two-level tree of strict \cite{BDPV11} duplexes
  over \Keccakp{} (\Cref{sec:tw128}): a serial root duplex that binds
  $(K, N, A)$, the first chunk, and the leaf tags into a single authentication
  tag, over a set of parallel, independently keyed leaf duplexes. All phases are
  domain-separated within one permutation, and the state is constant-size
  regardless of message length.

\item \textbf{All-in-one AE security.} We prove a concrete bound on the
  all-in-one AE advantage \cite{RS06} in the public-permutation model
  (\Cref{thm:ae}), obtained by composing random-oracle privacy and
  \textsf{INT-CTXT} bounds through the generic-composition argument of
  \cite{BN00} and lifting the result to the real permutation.

\item \textbf{Multi-user security.} We give a concrete multi-user
  indistinguishability bound \cite{BT16} for $D$ users
  (\Cref{thm:mu-ind}), obtained by a key-collision-stopped hybrid over the
  users that reuses the single-user privacy and \textsf{INT-CTXT} envelopes.

\item \textbf{Committing security.} We prove that \TW{} achieves $s$-way
  \textsf{CMTDs-4} committing security---commitment to the full
  $(K, N, A, M)$ input, for any number $s \geq 2$ of claimed openings---with a
  concrete root-collision bound (\Cref{cor:cmtds4}), and that it satisfies the
  stronger tag-committing notion, in which the $256$-bit root tag alone is a
  binding commitment to that input even when the claimed openings use distinct
  ciphertext bodies (\Cref{thm:tag-cmtds4}), matching the compactly committing
  AEAD goal of \cite{GLR17}. We derive the remaining
  \cite{BH22} committing notions (\textsf{CMT} and \textsf{CMTD} for
  $\ell \in \{1, 3, 4\}$) as direct bounds (\Cref{app:committing-transfer}).
  Committing security is native to the mode, with no generic transform.

\item \textbf{Context discoverability.} We prove that \TW{} resists context
  discovery in two forms. The first is a tag-target notion, \textsf{T-CDY}:
  given a target tag fixed in advance, no adversary can find a context and
  ciphertext body that decrypt successfully under it, with a concrete
  root-preimage bound
  (\Cref{thm:cdy}). This is the preimage counterpart of committing security and
  follows from the same sponge indifferentiability: the root tag is a
  preimage-resistant sponge output, leaving an adversary no better than a generic
  preimage search; \Cref{sec:related} contrasts this with the algebraic-MAC
  inversion that the \cite{MLGR23} discovery attacks exploit. The second is the
  published \cite{MLGR23} restricted notion $\mathsf{CDY}^\ast$ and its
  per-component variants $\mathsf{CDY}^\ast_k$, $\mathsf{CDY}^\ast_n$,
  $\mathsf{CDY}^\ast_a$, established with the same root tag through an added
  key-test term (\Cref{thm:cdy-full}). The tag-target and full-ciphertext
  notions are distinct---neither strengthens the other---so we prove both.

\item \textbf{Proof methodology.} We carry out the analysis in a dedicated \TW{}
  random-oracle model and transfer every bound to the public-permutation setting
  through the \cite{BDPV08} flat-sponge lift (\Cref{app:flat-sponge-lift}). A
  derived-adversary argument shows that each direct primitive query induces at
  most one random-oracle query, so the random-oracle envelopes are instantiated
  at the direct-query count $\Nprim$ rather than the total work $\Ntot$,
  separating the single capacity-birthday loss $\Lift_c(\Ntot)$ from the
  scheme-specific terms.

\item \textbf{Optimized implementations.} We describe and evaluate vectorized
  \texttt{amd64} (AVX-512 and AVX2) and \texttt{arm64} (NEON with the SHA-3
  extension) implementations whose batched leaf cores realize the tree's
  parallelism in practice, reaching multi-gigabyte-per-second throughput on
  contemporary hardware (\Cref{sec:performance}).
\end{itemize}

\subsection{Related Work}
\label{sec:related}

\paragraph{Sponge and duplex AEADs.}
Permutation-based authenticated encryption built on the sponge and duplex
constructions of \cite{BDPV08, BDPV11} is well established. Keyak \cite{BDPVV16}
is a CAESAR candidate built on the duplex over round-reduced \Keccak{}, whose
Motorist mode already admits parallel duplex instances. Ascon \cite{DEMS21}, the
lightweight winner of the CAESAR competition and the basis of the NIST
lightweight-cryptography standard, and Xoodyak \cite{DHPVV20}, a finalist in that
process whose Cyclist mode is a deliberately serial simplification of Motorist,
are duplex AEADs over the Ascon and Xoodoo permutations. \TW{} shares this
single-permutation, constant-state duplex foundation but differs in structure:
rather than one duplex session, it is a two-level tree whose leaves are
\emph{independently keyed} duplexes under domain-separated chunk identifiers.
Like Keyak's Motorist mode, the tree admits data-parallel evaluation across SIMD
lanes; the designs differ in where the degree of parallelism lives. Keyak fixes
it as a mode parameter---each named instance sets the number $\Pi$ of parallel
duplex instances across which a message is spread, so $\Pi$ is part of the wire
format and must be agreed by the encryptor and decryptor in advance. In \TW{} the
leaf decomposition is fixed by the mode, but the number of leaves evaluated
simultaneously is not part of the transcript: an implementation chooses it at run
time to match the host's vector width, and the ciphertext and tag are identical
however it is chosen, so a wide-SIMD encryptor and a scalar decryptor
interoperate.

\paragraph{Tree hashing.}
The two-level shape is inspired by tree hashing over the same permutation, in
particular KangarooTwelve \cite{BDPVVV16}, which splits its input into
fixed-size chunks hashed independently under \Keccakp{} and absorbs their
chaining values into a root node. \TW{} reuses the round count and the
final-node/leaf split of that design and adapts it to authenticated encryption:
each leaf chunk is encrypted and tagged independently, and the leaf tags are
absorbed by the root in place of chaining values. It also inherits the
short-message behavior of KangarooTwelve's \emph{kangaroo hopping}, which merges
the first chunk with the hashing of the remaining chunks' chaining values so
that an input fitting in a single chunk incurs no tree overhead: in \TW{} a
single-chunk message engages no leaf duplexes and no aggregation phase, the root
processing it directly and emitting the tag as a plain keyed duplex would. Short
messages therefore pay none of the tree's cost and retain the latency profile of
an unstructured duplex (\Cref{sec:latency}); the leaf layer, and its
parallelism, engage only once a message spans more than one chunk.

\paragraph{Committing AEAD.}
The study of committing authenticated encryption was initiated by \cite{GLR17},
who introduced compactly committing AEAD for message franking, and by
\cite{DGRW18}, who built it from a dedicated primitive (encryptment);
\cite{BH22} subsequently organized the notions into the \textsf{CMT-1}/\textsf{3}/\textsf{4}
and \textsf{CMTD} hierarchy and gave efficient generic transforms
(\textsf{UtC}, \textsf{RtC}, \textsf{HtE}) that add commitment to a base scheme.
A complementary line shows that widely used and dedicated AEADs fail these
notions: the invisible-salamander \cite{DGRW18} and partitioning-oracle
\cite{LGR21} attacks, multi-format ciphertexts \cite{ADGKLS22}, the
context-discovery and commitment attacks that break CCM, EAX, SIV, GCM, and
OCB3 \cite{MLGR23}, and an $O(1)$ key-committing attack against all variants of
AEGIS \cite{WP14} that refutes the prior belief that AEGIS was committing
\cite{IR23}. \cite{MLGR23} also introduce context discoverability, the
preimage facet of commitment, and show that their discovery attacks exploit
schemes whose authenticity is delegated to a non-preimage-resistant MAC such as
GHASH or CMAC. \TW{} instead targets both facets directly: its committing and
discoverability security follow from the indistinguishability of the sponge,
which makes the root tag collision- and preimage-resistant, rather than from a
generic transform applied to a non-committing base scheme. Because that tag is
a sponge output and not an invertible MAC, the discovery attacks of \cite{MLGR23}
have no analogue against \TW{}.

Closest to \TW{} is the recent work of \cite{DHMVV24}, which also builds
nonce-based AE natively on the SHA-3 functions \textsf{SHAKE} and
\textsf{TurboSHAKE}---the latter over the same round-reduced \Keccak{}
permutation as \TW{}---obtaining \textsf{CMT-4} from the collision resistance of
the underlying function rather than from a transform. Its schemes target
session-based communication and process each message through a sequential duplex
chain, whereas \TW{}, on the same native-committing single-permutation
foundation, is structured as a two-level tree whose independent leaves are
evaluated in parallel across SIMD lanes. The resulting throughput advantage on
large messages, and the session support \TW{} forgoes, are detailed in
\Cref{sec:compare-commit,sec:performance}.

\subsection{Paper Organization}
\label{sec:organization}

\Cref{sec:prelims} recalls the notation, sponge and duplex
constructions over \Keccak{}, the authenticated-encryption,
committing-security \cite{BH22}, and context-discoverability
\cite{MLGR23} notions used throughout, and the
multi-user indistinguishability notion of \cite{BT16}.
\Cref{sec:tw128} specifies the \TW{} construction and its parameters.
\Cref{sec:security-model} fixes the public-permutation games, the
intermediate random-oracle model, and the resource accounting that
all later bounds reference. \Cref{sec:main-results} states the
headline AE, mu-ind, CMTDs-4, T-CMTDs-4, and T-CDY theorems and their
concrete \TW{}-parameter forms; \Cref{sec:privacy,sec:authenticity}
prove the random-oracle privacy and INT-CTXT bounds that feed those
theorems, and \Cref{sec:cmtds3} proves the random-oracle
CMTDs-4, T-CMTDs-4, and T-CDY bounds. \Cref{sec:performance} reports the
performance of the reference and optimized implementations.
\Cref{sec:discussion} compares \TW{} to prior sponge AEADs and
committing constructions and discusses limitations.
\Cref{sec:conclusion} concludes.
\Cref{app:lemmas} collects the structural decoding and accounting
lemmas that form the proof core;
\Cref{app:flat-sponge-lift} carries out the \cite{BDPV08} flat-sponge lift
that converts each random-oracle bound to its public-permutation
form; \Cref{app:committing-transfer} gives the remaining
\cite{BH22} committing-security bounds; and
\Cref{app:test-vectors} lists \TW{} test vectors.
