\section{Preliminaries}
\label{sec:prelims}

\subsection{Notation}
\label{sec:notation}

\paragraph{Strings.}
Write $\bits$ for the binary alphabet. For an integer $n \geq 0$, $\bits^n$
denotes the set of $n$-bit strings, $\bits^* = \bigcup_{n \geq 0} \bits^n$
the set of all finite-length bit strings, and $\varepsilon$ the empty
string. For $x \in \bits^*$, $|x|$ is the bit length and $x \concat y$ is
the concatenation; the bitwise XOR of two equal-length strings $x, y \in
\bits^n$ is $x \oplus y$. A \emph{byte string} is an element of
$(\bits^8)^*$; its byte length is denoted $\|x\| = |x|/8$. For an
integer $0 \leq n < 2^{64}$, $\langle n \rangle_8 \in \bits^{64}$ is its
eight-byte little-endian encoding. For a finite or infinite bit string
$x$ and $0 \leq \tau \leq |x|$ when $x$ is finite,
$\lfloor x \rfloor_\tau \in \bits^\tau$ denotes the leading $\tau$ bits
of $x$.

\paragraph{Sampling and probability.}
We write $x \sample S$ for sampling $x$ uniformly at random from a finite
set $S$, with implicit coins independent across samples. For an event $E$
in a probability experiment, $\Pr[E]$ denotes its probability.

\paragraph{Sets of maps.}
For a set $S$, $\Perm(S)$ denotes the set of permutations on $S$; for a
positive integer $b$, $\Perm(\bits^b)$ is the set of $b$-bit
permutations.

\paragraph{Adversaries and games.}
An adversary $\mathcal{A}$ is a (possibly randomized) algorithm. A
\emph{game} $\mathsf{G}$ is an experiment that samples its private
randomness, runs $\mathcal{A}$ with access to a specified set of oracles
$O_1, \dots, O_k$, and returns a Boolean outcome. We write
$\mathcal{A}^{O_1, \dots, O_k}$ for the adversary's interface and
$\Pr[\mathsf{G}^{\mathcal{A}} \Rightarrow 1]$ for the probability that
$\mathsf{G}$ returns~$1$.

\paragraph{Advantages.}
For an indistinguishability-style experiment with two games $\mathsf{G}_0,
\mathsf{G}_1$, the distinguishing advantage of $\mathcal{A}$ against a
scheme $\Pi$ in security notion $\mathsf{X}$ is the absolute difference
\[
  \Adv^{\mathsf{X}}_\Pi(\mathcal{A})
  = \bigl| \Pr[\mathsf{G}_0^{\mathcal{A}} \Rightarrow 1]
         - \Pr[\mathsf{G}_1^{\mathcal{A}} \Rightarrow 1] \bigr|.
\]
For a one-shot or win-event experiment without a hidden challenge bit,
$\Adv^{\mathsf{X}}_\Pi(\mathcal{A})
= \Pr[\mathsf{G}^{\mathcal{A}} \text{ wins}]$, where
``$\mathsf{G}^{\mathcal{A}}$ wins'' denotes the event that the game
returns $1$. A bit-guessing experiment with a hidden challenge bit
instead uses the rescaled form
$\bigl|2 \Pr[\mathsf{G}^{\mathcal{A}} \text{ wins}] - 1\bigr|$, as in
the multi-user notion of \Cref{sec:mu-ind}.

\paragraph{Concrete security.}
All bounds in this paper are concrete: each advantage is an explicit
function of the resource caps introduced in
\Cref{sec:resources}. We make no use of asymptotic or negligibility
conventions.

\paragraph{Reference summary.}
\Cref{tab:notation} summarizes the resource caps and loss terms used
throughout. The caps are defined formally in \Cref{sec:resources}, the
loss terms in \Cref{sec:loss-terms}.

\begin{table}[ht]
  \centering
  \small
  \begin{tabular}{l l l}
    \toprule
    Symbol & Meaning & Defined \\
    \midrule
    $N$        & Construction-interface cost (\Keccak{} calls)       & \cref{sec:resources} \\
    $\Nprim$   & Direct primitive-interface queries                   & \cref{sec:resources} \\
    $\Ntot$    & $N + \Nprim$ (total query-sequence cost)             & \cref{sec:resources} \\
    $\qv$, $\Qv$ & Valid verification queries / cap (INT-CTXT)        & \cref{sec:resources} \\
    $\qRO$, $\QRO$ & Direct random-oracle queries / cap (RO-model)    & \cref{sec:resources} \\
    $\nleaf$, $\Nleaf$ & Distinct construction-generated final leaf transcripts / cap & \cref{sec:resources} \\
    \midrule
    $\Lift_c(\Ntot)$        & $\Ntot(\Ntot+1) / 2^{c+1}$, \cite{BDPV08} flat-sponge loss   & \cref{sec:loss-terms} \\
    $\KeyGuess_k(Q)$        & $Q / 2^k$, ideal-system key guess                       & \cref{sec:loss-terms} \\
    $\RootColl_\tau(Q, s)$  & $\binom{Q+s}{s} / 2^{\tau(s-1)}$, $s$-way root-collision & \cref{sec:loss-terms} \\
    $\RootPre_\tau(Q)$      & $(Q+1) / 2^{\tau}$, root-preimage / second-preimage      & \cref{sec:loss-terms} \\
    \bottomrule
  \end{tabular}
  \caption{Resource caps and loss terms.}
  \label{tab:notation}
\end{table}

\subsection{Sponges and Duplexes over \texorpdfstring{\Keccak{}}{Keccak-p}}
\label{sec:sponge}

\paragraph{The \Keccak{} permutation.}
The \Keccak{} family of permutations, introduced as part of the Keccak
design and standardized within FIPS~202~\cite{FIPS202}, is parameterized
by a state width $b$ and a round count $n_r$; we write $\Keccak[b, n_r]
\in \Perm(\bits^b)$ for the corresponding permutation. \TW{} uses
$\Keccak[1600, 12]$, the same primitive as
KangarooTwelve~\cite{BDPVVV16}, fixed throughout. In the
public-permutation security model of \Cref{sec:games-pp} and the
flat-sponge lift of \Cref{app:flat-sponge-lift}, this permutation is
modeled as a uniformly random element of $\Perm(\bits^{1600})$.

\paragraph{The sponge construction.}
Following \cite{BDPV08}, fix a permutation $\pi \in \Perm(\bits^b)$, a
\emph{sponge-compliant} padding rule $\mathsf{pad}$, and a rate $1 \leq
r < b$ with capacity $c = b - r$. A padding rule appends
$\mathsf{pad}[r](|M|)$, a bit string determined by the input length and
the rate, to an input $M$, extending it to a sequence of $r$-bit
blocks; it is sponge-compliant
\cite[Definition~1]{BDPV11} if $M \concat \mathsf{pad}[r](|M|)$ is never
empty and, for all $M \neq M'$ and all $n \geq 0$, $M \concat
\mathsf{pad}[r](|M|) \neq M' \concat \mathsf{pad}[r](|M'|) \concat
0^{nr}$. The sponge function $\Sponge[\pi, \mathsf{pad}, r]
: \bits^* \times \mathbb{N} \to \bits^*$ maps an input $M$ and an output
length $\ell$ to an $\ell$-bit string by absorbing $M \concat
\mathsf{pad}[r](|M|)$ into the all-zero $b$-bit state in $r$-bit blocks
(each separated by an application of $\pi$) and squeezing $\ell$ bits in
$r$-bit blocks from the resulting state. \cite[Theorem~2]{BDPV08} shows that
$\Sponge[\pi, \padten, r]$, where the simple rule $\padten$ appends a
single $1$ bit followed by the minimum number of $0$ bits reaching a
multiple of $r$, is indifferentiable from a random oracle when
$\pi$ is uniformly random. We bound its distinguishing advantage by
$\Lift_c(\Ntot) = \Ntot(\Ntot+1) / 2^{c+1}$, derived in
\Cref{sec:loss-terms} from the exact differentiating probabilities of
\cite[Lemmas~4 and~5]{BDPV08}.

\paragraph{The duplex construction.}
The \emph{duplex} construction of \cite{BDPV11} extends the sponge to
a stateful interface. A duplex object $\Duplex[\pi, \mathsf{pad}, r]$
is initialized to the all-zero state. Each call $\duplexing(\sigma,
\ell)$, with $\ell \leq r$, absorbs an input string $\sigma$ of at most
$\rho_{\max}(\mathsf{pad}, r)$ bits via $\pi$ and returns the first
$\ell$ bits of the resulting state. Here $\rho_{\max}(\mathsf{pad}, r)
= \min\{x : x + |\mathsf{pad}[r](x)| > r\} - 1$ is the largest input
length for which the padded input fits in a single $r$-bit block; for
the $\padtenone$ rule, $\rho_{\max}(\padtenone, r) = r - 2$
\cite{BDPV11}. \cite[Lemma~3]{BDPV11}
establishes the duplex-to-sponge equality: for any call
sequence $((\sigma_0, \ell_0), \dots, (\sigma_i, \ell_i))$, the $i$-th
output equals
\[
  \Sponge[\pi, \mathsf{pad}, r]\bigl(
    \sigma_0 \concat \mathsf{pad}_0 \concat \cdots \concat \sigma_i,\,
    \ell_i\bigr),
\]
where $\mathsf{pad}_j = \mathsf{pad}[r](|\sigma_j|)$ is the padding
the duplex appends in its $j$-th call; the flattened input carries
these interior paddings explicitly, and the sponge appends only the
final $\mathsf{pad}_i$. The flattening map is
injective by \cite[Lemma~4]{BDPV11}: the duplex-call sequence is
recoverable from the flattened sponge input.

\paragraph{\TW{} instantiation.}
\TW{} fixes the padding rule $\padtenone{}$ and the rate $r = 1344$, so
the capacity is $c = 256$ bits. The largest input length per duplex call
is therefore $\rho_{\max}(\padtenone, 1344) = 1342$ bits.

\paragraph{Bridge to the \texorpdfstring{$H$}{H}-input domain.}
The indifferentiability theorem of \cite{BDPV08} is stated for the
simpler $\padten{}$ padding over its unpadded $H$-input domain, while
\TW{} uses $\padtenone{}$ internally. \cite[Theorem~3]{BDPV11} supplies
an injective preprocessing bridge $\bridge[r, r_{\max}]$ between the two
domains. For \TW{}, $r = r_{\max} = 1344$, so the bridge reduces to
appending $1 \concat 0^q$ with $q$ determined by the input length modulo
$r_{\max}$; on the bridge image, $q$ is recovered as the trailing-zero
count. \Cref{sec:ro-model} instantiates this bridge on typed \TW{} duplex
transcript prefixes as the map $\flatmap(\cdot)$ used by the
random-oracle proofs of
\Cref{sec:privacy,sec:authenticity,sec:cmtds3,app:committing-transfer}.

\subsection{Authenticated Encryption with Associated Data}
\label{sec:ae-defs}

\paragraph{Syntax.}
A \emph{nonce-based authenticated-encryption scheme with associated
data} (AEAD scheme) is a pair $\SE = (\Enc, \Dec)$ of deterministic
algorithms with associated key space $\mathcal{K} \subseteq (\bits^8)^*$,
nonce space $\mathcal{N} \subseteq (\bits^8)^*$, associated-data space
$\mathcal{A} \subseteq (\bits^8)^*$, message space $\mathcal{M} \subseteq
(\bits^8)^*$, and ciphertext space $\mathcal{C} \subseteq (\bits^8)^*$. The
encryption algorithm $\Enc : \mathcal{K} \times \mathcal{N} \times
\mathcal{A} \times \mathcal{M} \to \mathcal{C}$ produces a ciphertext
$C = \Enc_K(N, A, M)$. The decryption algorithm $\Dec : \mathcal{K}
\times \mathcal{N} \times \mathcal{A} \times \mathcal{C} \to
\mathcal{M} \cup \{\bot\}$ returns either a plaintext or the
rejection symbol $\bot$. The \emph{tag length in bytes} is the constant
$\|\Enc_K(N, A, M)\| - \|M\|$, fixed by the scheme.
In this generic syntax, $C$ denotes the full AEAD ciphertext, including
any tag material. The \TW{} algorithm section (\Cref{sec:tw128}) writes this same value as
$C \concat T$, with $C$ the ciphertext body and $T$ the root tag.

\paragraph{Correctness.}
For every $(K, N, A, M) \in \mathcal{K} \times \mathcal{N} \times
\mathcal{A} \times \mathcal{M}$, $\Dec_K(N, A, \Enc_K(N, A, M)) = M$.

\paragraph{Privacy ($\mathsf{IND}\text{-}\$\text{-}\mathsf{CPA}$).}
The privacy game samples $K \sample \mathcal{K}$ and gives the
adversary $\mathcal{A}$ either the real encryption oracle
$\Enc_K(\cdot, \cdot, \cdot)$ or the random-output oracle $\Rand$
that, on every query $(N, A, M)$, returns a fresh uniformly random
byte string of length $\|\Enc_K(N, A, M)\| = \|M\| + \tau/8$ where
$\tau$ is the scheme's tag length in bits. The adversary is
\emph{nonce-respecting}: distinct encryption queries must use
distinct nonces. Define
\[
  \Advpriv_\SE(\mathcal{A})
  = \bigl|
    \Pr[\mathcal{A}^{\Enc_K} \Rightarrow 1]
    - \Pr[\mathcal{A}^{\Rand} \Rightarrow 1]
  \bigr|.
\]

\paragraph{Ciphertext integrity (INT-CTXT).}
The INT-CTXT game samples $K \sample \mathcal{K}$ and gives
$\mathcal{A}$ access to $\Enc_K$ and a verification oracle $\Ver_K$
that returns $1$ if $\Dec_K(N, A, C) \neq \bot$ and $0$ otherwise.
Each encryption query records the resulting tuple $(N, A, C)$. The
adversary wins if some verification query returns $1$ on a tuple
$(N, A, C)$ not previously recorded by the encryption oracle. No
nonce uniqueness is imposed on either oracle. Define
$\Advintctxt_\SE(\mathcal{A})$ as the probability that $\mathcal{A}$
wins.

\paragraph{All-in-one AE.}
The all-in-one authenticated-encryption notion of \cite{RS06},
instantiated for nonce-based AE following \cite{BT16}, combines
privacy and integrity into a single experiment. The
challenger samples $K \sample \mathcal{K}$ and grants $\mathcal{A}$
either the pair $(\Enc_K, \Ver_K)$ or the ideal pair $(\Rand,
\Replay)$. In the ideal pair, $\Rand$ returns a fresh uniformly
random byte string of length $\|\Enc_K(N, A, M)\|$ on each accepted
query $(N,A,M)$ and records the resulting tuple $(N,A,C)$ in a set
$W$; $\Replay_W(N,A,C)$ returns $1$ if $(N,A,C) \in W$ and $0$
otherwise. The adversary is nonce-respecting on encryption queries.
Define
\[
  \Advae_\SE(\mathcal{A})
  = \bigl|
    \Pr[\mathcal{A}^{\Enc_K, \Ver_K} \Rightarrow 1]
    - \Pr[\mathcal{A}^{\Rand, \Replay} \Rightarrow 1]
  \bigr|.
\]

\begin{lemma}[Bellare--Namprempre Composition]
\label{lem:bn-composition}
For every adversary $\mathcal{A}$ against the all-in-one AE security
of $\SE$, there exist adversaries $\mathcal{A}_{\text{priv}}$ and
$\mathcal{A}_{\text{int-ctxt}}$ with the same resources as
$\mathcal{A}$ such that
\[
  \Advae_\SE(\mathcal{A})
  \leq \Advpriv_\SE(\mathcal{A}_{\text{priv}})
   + \Advintctxt_\SE(\mathcal{A}_{\text{int-ctxt}}).
\]
\end{lemma}
\Cref{lem:bn-composition} is the all-in-one form of the
privacy-plus-integrity composition theorem of \cite{BN00}. The
standard proof inserts the hybrid $(\Enc_K, \Replay)$, where
$\Replay$ accepts exactly the tuples recorded by the real encryption
oracle. The hop from $(\Enc_K, \Ver_K)$ to $(\Enc_K, \Replay)$ is
bounded by INT-CTXT: the two interfaces differ only if verification
accepts a tuple not previously recorded by encryption. The hop from
$(\Enc_K, \Replay)$ to $(\Rand, \Replay)$ is bounded by privacy:
$\mathcal{A}_{\text{priv}}$ runs $\mathcal{A}$, forwards encryption
queries to its own oracle, records the returned tuples, and answers
verification queries by replay-table lookup. The lemma is applied in
the random-oracle model in the proof of \Cref{thm:ae}.

\subsection{Multi-User Indistinguishability}
\label{sec:mu-ind}

The multi-user indistinguishability notion of \cite[Fig.~3]{BT16} is
the multi-user lift of the single-user all-in-one notion of
\Cref{sec:ae-defs}. The number of users $u$ is adversary-determined:
it is the number of $\mathsf{New}$ queries the adversary makes, i.e.,
the final value of the user counter $v$ in the game below. A challenge bit $b \sample \bits$ selects between the
real construction interface (real ciphertexts, real verification) and
an ideal interface (uniform strings of matching length, verification
that accepts only previously-issued encryption tuples). The adversary
also accesses an ideal primitive interface, shared between the two
worlds. The adversary outputs a guess $b'$ and wins if $b' = b$.

\paragraph{Game.}
The game $\mathsf{G}^{\mathsf{mu\text{-}ind}}_\SE(\mathcal{A})$ of
\cite[Fig.~3]{BT16} samples $b \sample \bits$ and maintains a user
counter $v$, a set $V$ of $(d, N)$ pairs already used by encryption,
and a set $W$ of recorded encryption tuples $(d, N, C, A)$. We write
the user index as $d$ and the associated-data input as $A$, where
\cite{BT16} writes $i$ and $H$ respectively, to match the notation of
\Cref{sec:mu-setting}; unlike \cite{BT16}, whose advantage is the
signed quantity $2\Pr[\mathsf{G}] - 1$, we take the absolute value so
that the advantage equals the two-game distinguishing form below. The adversary has access to
\begin{itemize}
\item $\mathsf{New}()$: increment $v$, sample $K_v \sample
  \mathcal{K}$.
\item $\mathsf{Enc}(d, N, M, A)$: reject inactive users and repeated
  user-nonce pairs. Otherwise compute $C_1 = \Enc_{K_d}(N, A, M)$,
  sample $C_0 \sample \bits^{8\|C_1\|}$, record $(d, N)$ in $V$ and
  $(d, N, C_b, A)$ in $W$, and return $C_b$.
\item $\mathsf{Vf}(d, N, C, A)$: reject if $d \notin \{1, \dots,
  v\}$; if $(d, N, C, A) \in W$ return $\mathsf{true}$; if $b = 0$
  return $\mathsf{false}$; else return $[\Dec_{K_d}(N, A, C) \neq
  \bot]$.
\item The shared ideal primitive interface.
\end{itemize}
The adversary outputs $b' \in \bits$ and the game returns $1$ if
$b' = b$ and $0$ otherwise. The advantage is
\[
  \Advmuind_\SE(\mathcal{A})
  = \left|2 \Pr[\mathsf{G}^{\mathsf{mu\text{-}ind}}_\SE(\mathcal{A})
          \text{ returns } 1] - 1\right|.
\]

\paragraph{Equivalence with the two-game form.}
Since $b$ is uniform, a standard calculation gives
\[
  \Advmuind_\SE(\mathcal{A})
  = \bigl|
      \Pr[\mathcal{A}^{\mathsf{Enc}, \mathsf{Vf}, b=1} \Rightarrow 1]
      - \Pr[\mathcal{A}^{\mathsf{Enc}, \mathsf{Vf}, b=0} \Rightarrow 1]
    \bigr|,
\]
so $\Advmuind_\SE$ coincides with the two-game distinguishing
advantage between the real $(\Enc, \Ver)$ pair and the ideal
$(\Rand, \Replay)$ pair, instantiated per user. The single-user case
$u = 1$ recovers the all-in-one AE notion
used in \Cref{sec:ae-defs}, augmented with the ideal primitive
interface present in both worlds; in particular, $\Advmuind$
generalizes $\Advae$, since an all-in-one adversary embeds into the
$u = 1$ game with identical advantage by making no primitive queries.

\paragraph{Per-user nonce uniqueness.}
Nonce uniqueness is enforced per user via the set $V$: the same nonce
may appear under distinct users but not twice under the same user.
This is strictly weaker than the global nonce-uniqueness requirement
that would force every $(d, N)$ pair across all users to be unique.

The multi-key committing-security story does not need a separate
multi-user notion: the $s$-way CMTDs-$\ell$ games of
\Cref{sec:commit-defs} already grant the adversary full control of
all $s$ keys, so they are themselves the multi-key committing
statement.

\subsection{Committing Security and Context Discoverability}
\label{sec:commit-defs}

\cite{BH22} formalize a family of committing-security notions for
nonce-based AEAD schemes, parameterized by how much of the
encryption input is committed and by whether commitment is
established through decryption (the D-notions) or through encryption
agreement (the E-notions). We recall their definitions and the
$s$-way generalization used throughout this paper, then recall the
complementary \emph{context-discoverability} notion of \cite{MLGR23}.
The two capture orthogonal facets of commitment: committing security is
a collision requirement on the map from contexts to ciphertexts, while
context discoverability is the corresponding preimage requirement.

\paragraph{What-is-committed functions.}
For $\ell \in \{1, 3, 4\}$, the \emph{what-is-committed} function
$\WiC_\ell$ projects an encryption input $(K, N, A, M) \in \mathcal{K}
\times \mathcal{N} \times \mathcal{A} \times \mathcal{M}$ to the
portion it should commit:
\[
\begin{aligned}
  \WiC_1(K, N, A, M) &= K, \\
  \WiC_3(K, N, A, M) &= (K, N, A), \\
  \WiC_4(K, N, A, M) &= (K, N, A, M).
\end{aligned}
\]

\paragraph{CMTD-$\ell$ and CMT-$\ell$ (two-key form).}
Following \cite[Fig.~4]{BH22}, the two-key CMTD-$\ell$
game samples no key. The adversary outputs a ciphertext $C$ together
with two tuples $(K_1, N_1, A_1, M_1), (K_2, N_2, A_2, M_2)$ with
$\WiC_\ell(K_1, N_1, A_1, M_1) \neq \WiC_\ell(K_2, N_2, A_2, M_2)$,
and wins if $\Dec_{K_i}(N_i, A_i, C) = M_i$ for both $i \in \{1,
2\}$. The CMT-$\ell$ game has the adversary output the
two tuples (without $C$); the adversary wins if $\Enc_{K_1}(N_1, A_1, M_1) =
\Enc_{K_2}(N_2, A_2, M_2)$. No tuple entry is allowed to be $\bot$
and all entries must lie in the scheme's syntactic domain. Define
$\Adv^{\mathsf{CMTD}\text{-}\ell}_\SE(\mathcal{A})$ and
$\Adv^{\mathsf{CMT}\text{-}\ell}_\SE(\mathcal{A})$ as the
probabilities that the adversary wins the respective game.

\paragraph{$s$-way generalization.}
For $s \geq 2$, \cite[Fig.~5]{BH22} extends the games to tuples
$(K_i, N_i, A_i, M_i)_{i=1}^s$ with pairwise distinct
$\WiC_\ell$-images. The $s$-way CMTDs-$\ell$ game has the adversary
output a ciphertext $C$ alongside the tuples and returns $1$ if
$\Dec_{K_i}(N_i, A_i, C) = M_i$ for every $i$. The $s$-way
CMTs-$\ell$ game returns $1$ if all encryptions
$\Enc_{K_i}(N_i, A_i, M_i)$ are equal. The two-tuple case $s = 2$
recovers CMTD-$\ell$ and CMT-$\ell$. Advantages
$\Advcmtds{\ell}_\SE(\mathcal{A})$ and
$\Advcmts{\ell}_\SE(\mathcal{A})$ are the probabilities that the
adversary wins the respective $s$-way game; the parameter $s$ is
suppressed from the notation when clear from context. The
CMTDs-$\ell$ and CMTs-$\ell$
definitions are instantiated for \TW{} in \Cref{sec:games-pp}, with the
public-permutation lift deferred to that section.

\paragraph{Relations.}
\cite[Figs.~4 and~5]{BH22} record the implications among the notions.
For the D-notions we use:
\[
  \mathsf{CMTDs}\text{-}3 \;\Rightarrow\;
  \mathsf{CMTDs}\text{-}\ell \text{ for } \ell \in \{1, 4\}
\]
(the $\ell = 1$ case is immediate since pairwise
distinct keys imply pairwise distinct $(K, N, A)$ triples; the
$\ell = 4$ case uses deterministic decryption, as
recalled in \Cref{app:committing-transfer}). The E-notions are bounded
directly in \Cref{app:committing-transfer} by the same final-root
candidate-collision argument, rather than through an encryption reduction.

\paragraph{Context discoverability.}
Where committing security forbids two contexts from colliding on one
ciphertext, \emph{context discoverability} \cite{MLGR23} forbids an
adversary from \emph{finding} a decrypting context for a target
ciphertext: it is to committing security what preimage resistance is to
collision resistance. Following the query-independent context selector
of \cite{MLGR23}, the discoverability game is given a target ciphertext
fixed independently of the scheme's primitive and asks the adversary to
output a decryption context under which that ciphertext decrypts without
error. The notion is parameterized by which components of the context
the selector fixes and which the adversary supplies; the unrestricted
form, in which the adversary supplies the entire context, dominates the
restricted variants of \cite{MLGR23}, in which the selector additionally
pins two of the three context components and the adversary supplies only
the remaining one. \cite{MLGR23} show that schemes which
delegate authenticity to a non-preimage-resistant MAC, including
\textsf{CCM}, \textsf{EAX}, \textsf{SIV}, \textsf{GCM}, and
\textsf{OCB3}, admit efficient discoverability attacks. A closely
related preimage requirement fixes a target tag that is itself a genuine
encryption output, rather than a primitive-independent constant, and
forbids finding a \emph{distinct} opening of that realized tag; this
second-preimage variant, in the everywhere (eSec) sense of \cite{RS04}, is not
subsumed by the query-independent discoverability notion---the realized
tag is correlated with the primitive---and is the relevant notion when a
higher-level protocol signs or commits to an honestly produced tag. The notion is
instantiated for \TW{} in \Cref{sec:games-pp}; its preimage character
is what makes \TW{}'s root tag, a sponge image rather than an invertible
MAC, resist these attacks, in both the query-independent and
realized-target forms.
