\section{The TW128 Construction}
\label{sec:tw128}

\subsection{Design Overview}
\label{sec:design}

\TW{} is a nonce-based authenticated encryption scheme with associated
data, built as a two-level tree of duplex objects over the
\Keccakp{} permutation. A single \emph{root} duplex, initialized
with the key $K$ and nonce $U$, absorbs the associated data $A$ when it
is nonempty, emits
keystream for the first plaintext chunk $M_0$ of at most $\beta$ bytes,
and absorbs the resulting ciphertext chunk $C_0$;
when $A$ is empty the associated data phase is elided and the
initialization call itself emits the initial $M_0$ keystream;
the remaining plaintext is partitioned into \emph{leaf} chunks
$M_1, \dots, M_n$, each handled by an independent leaf duplex
initialized with $(K, U, j)$. The leaf duplex emits the keystream for
$M_j$, absorbs the resulting ciphertext chunk $C_j$, and produces a
$\tauleaf$-bit leaf tag $T_j$. When $n \geq 1$ the leaf tags, together
with the eight-byte little-endian leaf count $\langle n \rangle_8$, are
absorbed into the root duplex, which emits a single $\tauroot$-bit root
tag $T$; when $n = 0$ the aggregation phase is elided and the closing
message phase call of the root chunk emits $T$ directly, mirroring the
way a leaf duplex emits its leaf tag. The construction is depicted in
\Cref{fig:tw128-tree}.

Three design properties motivate the tree shape. First, the leaf
duplexes operate on disjoint state and consume disjoint inputs once
$(K, U)$ is fixed, so leaves $1, \dots, n$ can be evaluated in parallel.
The transcript fixes the leaf decomposition and order, but not the number
of leaves an implementation evaluates at once; scalar, SIMD, and multicore
implementations therefore produce the same ciphertexts and tags.
\Cref{sec:performance} quantifies the resulting throughput on AMD64 and
ARM64 hardware. Second, every duplex operates on a bounded $1600$-bit
state regardless of message length, and the leaf tags are aggregated as a
stream rather than buffered in full (\Cref{sec:enc}), so the working
memory is constant in $\|M\|$ at a fixed degree of parallelism, scaling
only with the number of leaves evaluated simultaneously. Third, the
explicit aggregation of leaf tags through a single deterministic root
transcript is the AEAD analog of KangarooTwelve's final-node hashing of
per-chunk chaining values. In \TW{}, the chaining values are the leaf tags
and the final digest is the root tag. This makes the root tag the natural
hash point for the full $(K, U, A, M)$ context; the formal hash,
committing analysis appears in \Cref{sec:root-tag-hash-security}.

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
    font=\small,
    >=Stealth,
    block/.style={draw, rounded corners=1pt, minimum height=10mm,
                  align=center},
    init/.style={block, minimum width=15mm, fill=black!10,
                 font=\footnotesize},
    msg/.style={block, minimum width=11mm, fill=blue!12},
    cv/.style={block, minimum width=9mm, fill=green!18,
               font=\footnotesize},
    enc/.style={block, minimum width=11mm, fill=black!10,
                font=\scriptsize},
    leaf/.style={block, minimum height=22mm, minimum width=11mm,
                 fill=blue!12},
    arr/.style={->, thin},
    flab/.style={font=\scriptsize, inner sep=1pt},
  ]
    \node[init] (init) {$K, U$};
    \node[msg, right=1mm of init] (ad) {$A$};
    \node[msg, right=1mm of ad] (c0) {$C_0$};
    \node[cv, right=1mm of c0] (t1) {$T_1$};
    \node[cv, right=1mm of t1] (t2) {$T_2$};
    \node[right=1mm of t2, inner sep=1pt] (dots) {$\cdots$};
    \node[cv, right=1mm of dots] (tn) {$T_n$};
    \node[enc, right=1mm of tn] (lenc) {$\langle n \rangle_8$};

    \draw[arr] (lenc.east) -- ++(7mm,0) node[right] {$T$};

    \node[leaf, above=12mm of t1] (leaf1) {$C_1$};
    \node[leaf, above=12mm of t2] (leaf2) {$C_2$};
    \node[leaf, above=12mm of tn] (leafn) {$C_n$};

    \node[flab, above=1mm of leaf1.north] {$K, U, 1$};
    \node[flab, above=1mm of leaf2.north] {$K, U, 2$};
    \node[flab, above=1mm of leafn.north] {$K, U, n$};

    \draw[arr] (leaf1.south) -- (t1.north);
    \draw[arr] (leaf2.south) -- (t2.north);
    \draw[arr] (leafn.south) -- (tn.north);
  \end{tikzpicture}
  \caption{Schematic of TW128 for $n \geq 1$ leaves.
    The root duplex (bottom row) is
    initialized with $(K, U)$ and absorbs in turn the associated data
    $A$, the root ciphertext chunk $C_0$, each leaf tag
    $T_1, \dots, T_n$, and the eight-byte little-endian leaf count
    $\langle n \rangle_8$; it emits the root tag $T$. Each leaf duplex
    (top row) is initialized with $(K, U, j)$, emits keystream for
    plaintext chunk $M_j$, absorbs the resulting ciphertext chunk $C_j$,
    and produces $T_j$. Leaves can be evaluated in parallel. The
    ciphertext chunks $C_0, C_1, \dots, C_n$ are obtained by XORing the
    keystream emitted by the corresponding duplex with the plaintext
    chunks $M_0, M_1, \dots, M_n$. When $n = 0$ the diagram
    reduces to the bottom row without any $T_j$ boxes or aggregation
    block: the aggregation phase is elided and the closing message phase
    call on $C_0$ emits the root tag $T$ directly. When the
    associated data is empty the $A$ block is absent: the
    associated data phase is elided and the initialization call emits the
    initial $M_0$ keystream directly.}
  \label{fig:tw128-tree}
\end{figure}

\subsection{Parameters and Domain}
\label{sec:params}

\Cref{tab:params} lists the user-visible and derived scheme parameters.
The implementation uses the same byte length for the root tag and each
leaf tag, but the proofs of \Cref{sec:aead-security,sec:root-tag-hash-security} keep
$\tauroot$ and $\tauleaf$ as separate symbols.

\begin{table}[ht]
  \centering
  \small
  \begin{tabular}{l l l}
    \toprule
    Parameter & Value & Description \\
    \midrule
    $k$                  & $256$          & Key length (bits) \\
    $\nu$                & $256$          & Nonce length (bits) \\
    $\tauroot$ & $256$          & Root tag length (bits) \\
    $\tauleaf$ & $256$          & Leaf tag length (bits) \\
    $\beta$              & $8183$         & Plaintext chunk size (bytes) \\
    $M_{\max}$           & $8183 \cdot 2^{64}$ bytes & Maximum plaintext length \\
    $A_{\max}$           & $8183 \cdot 2^{64}$ bytes & Maximum associated data length \\
    \midrule
    $b$           & $1600$  & Permutation state width (bits) \\
    $n_r$         & $12$    & Permutation rounds \\
    $r$           & $1344$  & Sponge rate (bits) \\
    $c$           & $256$   & Sponge capacity (bits) \\
    $\rho$        & $167$   & Maximum byte-aligned absorption per duplex call (bytes) \\
    \bottomrule
  \end{tabular}
  \caption{\TW{} parameters.}
  \label{tab:params}
\end{table}

The bound $M_{\max} = 8183 \cdot 2^{64}$ bytes is the largest plaintext whose leaf
index fits in $\langle \cdot \rangle_8$: writing $\leaves(M) =
\max(0, \lceil \|M\| / \beta \rceil - 1)$, every
supported plaintext satisfies $0 \leq \leaves(M) \leq 2^{64} - 1$, so
leaf indices lie in $\{1, \dots, 2^{64} - 1\}$. The associated data
bound $A_{\max}$ is a fixed scheme parameter taken equal to $M_{\max}$
unless stated otherwise. Inputs exceeding these bounds are outside the
scheme domain.

The derived per-call absorption bound $\rho$ follows the \cite{BDPV11}
analysis: with $r = 1344$ and $\padtenone$ padding, $\rho_{\max}(\padtenone, r) =
r - 2 = 1342$ bits. The byte-aligned data field shares this allotment
with the four-bit phase suffix of \Cref{sec:domain-sep}, so $\rho$ is
the largest integer satisfying $8\rho + 4 \leq 1342$, giving $\rho =
167$ data bytes (and $8\rho + 4 = 1340 \leq 1342$).

\subsection{Parameter Choice Rationale}
\label{sec:param-rationale}

The four free parameters $c$, $k$, $\tauroot =
\tauleaf$, and $\beta$ (the rate $r = b - c$ is then determined by
the capacity) are chosen to give 128-bit
single-key security against every term of the concrete bounds derived
in \Cref{sec:concrete} while keeping per-byte cost low; the nonce
width $\nu$ is fixed separately, by the headroom the wide permutation
affords. Specifically:

\begin{itemize}
\item $c = 256$. The dominant single-key term is the \cite{BDPV08}
flat sponge loss
\[
  \Lift_c(\Ntot) = \Ntot(\Ntot+1)/2^{c+1},
\]
which reaches the $2^{-128}$ threshold at
$\Ntot \approx 2^{(c-127)/2} \approx 2^{64.5}$ \Keccakp{} calls;
the work cap $\Ntot \leq 2^{63}$ used in \Cref{sec:concrete-claim} keeps
this term at most $2^{-131}+2^{-194}$, and hence below $2^{-130}$.
Setting $c = 256$ thereby delivers 128-bit single-key security on this term.
Under the mu-ind
bound of \Cref{sec:aead-security} the per-user security margin degrades by
$\log D$ bits in $D$ users; the concrete $D$-indexed bound appears in
\Cref{sec:concrete-claim}.

\item $r = 1344$. With state width $b = 1600$ fixed by the
\Keccakp{} choice, $r = b - c = 1344$ is the largest rate
compatible with the chosen capacity. The 12-round
\Keccakp{} permutation matches KangarooTwelve's
choice~\cite{BDPVVV16}; \TW{} adopts that established tree-hashing
parameter rather than introducing a new reduced-round setting.

\item $\tauroot = \tauleaf = 256$. Matching the
capacity ensures that the per-tag collision terms in the
authenticity and committing bounds (\Cref{sec:concrete}) are dominated
by the capacity birthday rather than the tag length.

\item $k = 256$. Matching the capacity ensures that the per-user key
guess
\[
  \KeyGuess_k(\Nprim) = \Nprim/2^k
\]
remains below the capacity birthday at the target $D$ of
\Cref{sec:concrete-claim}.

\item $\beta = 8183$. The chunk size is set to $49\rho = 49 \cdot 167$
bytes, the largest multiple of the per-call absorption bound $\rho$ not
exceeding $2^{13}$ bytes. Taking $\beta$ to be an exact multiple of
$\rho$ makes every full leaf split into exactly $49$ fully utilized
message duplex calls with no short final block, so a full leaf costs one
initialization duplex call plus $49$ message duplex calls. This amortizes
the fixed per-leaf initialization cost over a large chunk while keeping
the leaf state working set ($8183 < 2^{13}$ bytes) small enough for L1
cache; \Cref{sec:throughput} reports the resulting cycles-per-byte figures.

\item $\nu = 256$. The nonce width is not constrained by the concrete
bounds, which assume a nonce-respecting adversary; it is set generously
because the wide permutation makes a wide nonce nearly free. The root
initialization absorbs $\prfxroot \concat K \concat U$, $560$ bits in
all, in a single duplex call, comfortably within the $1336$-bit
($\rho = 167$-byte) data field (\Cref{sec:params}), so widening the
nonce to $256$ bits adds neither a permutation call nor any per-message
cost. The width also removes any practical concern over random nonce
collisions: a uniformly random $256$-bit nonce repeats over $q$
messages with probability at most $\binom{q}{2}/2^{256}$, negligible at
the work cap of \Cref{sec:concrete-claim}. Deployments that do not
require a full-width random nonce lose nothing by the choice: a
narrower nonce---a $96$-bit packet counter, say---is carried in the
fixed $\nu$-bit field by zero-padding, so a single mode serves both
random nonce and counter-based settings with no change of parameters.
\end{itemize}

\subsection{Domain Separation}
\label{sec:domain-sep}

Distinct duplex instances and distinct phases within a duplex are kept
separate at the transcript level by two mechanisms. First, the
initialization strings carry a 6-byte ASCII prefix and, for leaves, an
eight-byte little-endian chunk index:
\begin{align*}
  \prfxroot &= \texttt{"TW128R"} \in \bits^{48}, \\
  \prfxleaf &= \texttt{"TW128L"} \in \bits^{48}.
\end{align*}
The root duplex's first absorbed string is
$\prfxroot \concat K \concat U$, and the $j$-th leaf
duplex's first absorbed string is $\prfxleaf \concat K
\concat U \concat \langle j \rangle_8$. Together with the fixed
$k$-bit and $\nu$-bit widths of $K$ and $U$, these prefixes separate
root from leaf transcripts and distinguish leaves with different
chunk indices.

Second, every byte-aligned absorption carries a four-bit phase suffix.
We identify each suffix with the four-bit string given by its
\Cref{tab:suffixes} value written least significant bit first, so that a
duplex call absorbing a byte-aligned block $\sigma$ under a phase
suffix \sigph{} feeds the duplex interface of \Cref{sec:sponge} the input
$\sigma \concat \sigph$ before $\padtenone$ padding.
The seven phase suffixes are summarized in \Cref{tab:suffixes}; they
correspond to initialization, non-final and final associated data
blocks, non-final and final message blocks, and non-final and final
aggregation blocks. The seven values are pairwise distinct, so any two
transcripts that differ in the phase of any block also differ in the
flattened sponge input.

\begin{table}[ht]
  \centering
  \small
  \begin{tabular}{l l l}
    \toprule
    Name & Hex & Use \\
    \midrule
    \siginit & \texttt{0xC} & End of initialization (the sole init call) \\
    \sigadmore   & \texttt{0x9} & Non-final associated data block \\
    \sigadlast   & \texttt{0xD} & Final associated data block \\
    \sigmsgmore  & \texttt{0xA} & Non-final message block \\
    \sigmsglast  & \texttt{0xE} & Final message block \\
    \sigaggmore  & \texttt{0xB} & Non-final aggregation block \\
    \sigagglast  & \texttt{0xF} & Final aggregation block (emits root tag) \\
    \bottomrule
  \end{tabular}
  \caption{Phase suffixes (4 bits each, appended LSB-first).}
  \label{tab:suffixes}
\end{table}

\Cref{tab:transcript-schedule} summarizes the root and leaf transcript
schedule. The algorithms of \Cref{sec:enc,sec:dec} give the normative
byte-level specification; the table records which phase is present and what
output the final call of that phase supplies.

\begin{table}[ht]
  \centering
  \scriptsize
  \setlength{\tabcolsep}{1pt}
  \begin{tabular}{@{}p{0.10\linewidth}p{0.11\linewidth}p{0.13\linewidth}p{0.26\linewidth}p{0.24\linewidth}p{0.09\linewidth}@{}}
    \toprule
    Instance & Phase & Suffixes & Absorbed string & Output supplied & When \\
    \midrule
    Root
      & Init
      & \siginit
      & $\prfxroot \concat K \concat U$
      & $0$ if $A \neq \varepsilon$; otherwise first $M_0$ keystream
      & Always \\
    Root
      & AD
      & \sigadmore, \sigadlast
      & $\rho$-byte block partition of $A$
      & Final call emits first $M_0$ keystream
      & $A \neq \varepsilon$ \\
    Root
      & Message
      & \sigmsgmore, \sigmsglast
      & $\rho$-byte block partition of $C_0$
      & Non-final calls emit next keystream; final call emits $T$ if $n=0$,
        and $0$ otherwise
      & Always \\
    Leaf $j$
      & Init
      & \siginit
      & $\prfxleaf \concat K \concat U \concat \langle j \rangle_8$
      & First $M_j$ keystream
      & $1 \leq j \leq n$ \\
    Leaf $j$
      & Message
      & \sigmsgmore, \sigmsglast
      & $\rho$-byte block partition of $C_j$
      & Non-final calls emit next keystream; final call emits $T_j$
      & $1 \leq j \leq n$ \\
    Root
      & Aggregation
      & \sigaggmore, \sigagglast
      & $T_1 \concat \cdots \concat T_n \concat \langle n \rangle_8$
      & Final call emits $T$
      & $n \geq 1$ \\
    \bottomrule
  \end{tabular}
  \caption{\TW{} transcript schedule. ``First $M_i$ keystream'' means
    $8\min(\|M_i\|,\rho)$ output bits for the first duplex block of that
    message chunk; subsequent message-phase outputs have the length of the next
    duplex block, as in \Cref{alg:helpers}.}
  \label{tab:transcript-schedule}
\end{table}

The combined effect of the initialization prefixes and the phase
suffixes is that the flattened sponge input of any \TW{} duplex call
uniquely determines the duplex instance, the leaf index when applicable,
the phase, and the duplex-call position within that phase.
\Cref{def:wf-transcripts} (Well-formed \TW{} transcript prefixes),
\Cref{lem:transcript-inj} (Transcript Injectivity), and its structural
corollaries formalize this parsing fact for the proofs of
\Cref{sec:aead-security,sec:root-tag-hash-security} and
\Cref{cor:committing-combined}.

\subsection{Encryption}
\label{sec:enc}

\Cref{alg:enc} specifies $\Enc_K(U, A, M)$ in terms of two
helper procedures, \Call{Absorb}{} and \Call{StreamEnc}{}, defined in
\Cref{alg:helpers}. These helpers sit below the tree layer: only
\Cref{alg:enc,alg:dec} split messages or ciphertexts into $\beta$-byte
root and leaf chunks, while the helpers split an already chosen byte
string into $\rho$-byte duplex blocks. \Call{Absorb}{} drives a duplex
through a sequence of such blocks with non-final $\sigma^-$ and final
$\sigma^+$ suffix tags, returning the output of the final call; the
empty-input case yields a single empty duplex block carrying the
$\sigma^+$ tag. The streaming helpers use the same empty-input
convention, so a zero-length message string still performs one final
message phase duplex call and returns a zero-length body.
\Cref{alg:enc} invokes \Call{Absorb}{} for the associated data phase
only when $A \neq \varepsilon$; when $A = \varepsilon$ the phase is
elided and the root \siginit call emits the initial $M_0$ keystream
directly.
\Call{StreamEnc}{} encrypts a plaintext byte string one duplex block at
a time, XORing each block with the current keystream, absorbing
the resulting ciphertext duplex block back into the duplex with the
appropriate phase tag, and using the duplex's output as the next
keystream. This is
the duplex-level presentation of the
overwrite mechanism of \cite[\S6.2 and Algorithm~5]{BDPV11}: when the
current rate prefix emitted as keystream is $Z$, XOR-absorbing
$m \oplus Z$ has the same update on the message bytes as overwriting
that prefix with $m$, with the phase tag still carried as part of the
duplex input. The decryption helper \Call{StreamDec}{} is identical to
\Call{StreamEnc}{} with the roles of the plaintext and ciphertext duplex
blocks exchanged: it takes ciphertext duplex blocks $c_i$ as input,
recovers each plaintext duplex block as $m_i = c_i \oplus Z$, absorbs the
same $c_i$ under the same phase suffix, and returns
$(m_1 \concat \cdots \concat m_t, Z')$; we omit its pseudocode. In both
helpers, each duplex call absorbs a
duplex block followed by its phase suffix---$\sigma^-$ for a non-final
block and $\sigma^+$ for the final block---and requests the output bits
the caller consumes next: $\ell$ (possibly zero) on the final call, and
the next duplex block's keystream length on non-final calls. Each call is
the duplex interface of
\Cref{sec:sponge} applied to the suffixed input of \Cref{sec:domain-sep}.

The encryption procedure (\Cref{alg:enc}) instantiates the root duplex
and obtains the initial keystream for the root chunk $M_0$: when $A \neq
\varepsilon$ it absorbs the associated data $A$, and when $A =
\varepsilon$ it elides the associated data phase and takes the keystream
from the \siginit call itself. It then encrypts $M_0$ while absorbing
the resulting ciphertext chunk $C_0$. When $n = 0$ the closing
\sigmsglast call of this root chunk requests $\tauroot$ output bits,
which are the root tag $T$, and the aggregation phase is elided. When
$n \geq 1$ it independently encrypts each leaf chunk
$M_j$ while absorbing $C_j$, producing the leaf tag $T_j$; the leaf
tags together with $\langle n \rangle_8$ are then absorbed into the root
duplex, and the final \sigagglast call emits the root tag $T$. The
ciphertext is the concatenation $C_0 \concat C_1 \concat \cdots \concat
C_n$. Thus this section writes $C$ for the ciphertext body and
$C \concat T$ for the full AEAD ciphertext returned by $\Enc_K(U,A,M)$.

\begin{algorithm}[t]
  \caption{TW128 helper procedures.}
  \label{alg:helpers}
  \begin{algorithmic}[1]
    \Procedure{Absorb}{$D$, $s$, $\sigma^-$, $\sigma^+$, $\ell$}
      \State Partition $s$ into duplex blocks $s_1, \dots, s_t$ of exactly
        $\rho$ bytes each, except that the last block may be shorter.
      \State Require $t \geq 1$; the empty case yields the single empty
        duplex block $s_1 = \varepsilon$.
      \For{$i \gets 1$ \textbf{to} $t - 1$}
        \State $D.\duplexing(s_i \concat \sigma^-, 0)$
      \EndFor
      \State \Return $D.\duplexing(s_t \concat \sigma^+, \ell)$
    \EndProcedure
    \Statex
    \Procedure{StreamEnc}{$D$, $m$, $Z$, $\sigma^-$, $\sigma^+$, $\ell$}
      \State Partition $m$ into duplex blocks $m_1, \dots, m_t$ of exactly
        $\rho$ bytes each, except that the last block may be shorter.
      \State Require $t \geq 1$; if $m = \varepsilon$, set $t = 1$ and
        $m_1 = \varepsilon$.
      \For{$i \gets 1$ \textbf{to} $t - 1$}
        \State $c_i \gets m_i \oplus Z$
        \State $Z \gets D.\duplexing(c_i \concat \sigma^-, 8\|m_{i+1}\|)$
      \EndFor
      \State $c_t \gets m_t \oplus Z$
      \State $Z' \gets D.\duplexing(c_t \concat \sigma^+, \ell)$
      \State \Return $(c_1 \concat \cdots \concat c_t, Z')$
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
  \caption{$\Enc_K(U, A, M)$.}
  \label{alg:enc}
  \begin{algorithmic}[1]
    \Require $K \in \bits^k$, $U \in \bits^{\nu}$, $A$ with $\|A\| \leq A_{\max}$, $M$ with $\|M\| \leq M_{\max}$.
    \Ensure $C \concat T$ with $\|C\| = \|M\|$ and $T \in \bits^{\tauroot}$.
    \State $M_0 \gets$ first $\min(\|M\|, \beta)$ bytes of $M$ (possibly $\varepsilon$).
    \State Partition the remaining suffix into chunks $M_1, \dots, M_n$ of exactly $\beta$ bytes each, except that the last chunk may be shorter but nonempty, so $n = \leaves(M)$.
    \State $D_{\text{root}} \gets$ new $\Duplex$
    \If{$A = \varepsilon$}
      \State $Z \gets D_{\text{root}}.\duplexing(\prfxroot \concat K \concat U \concat \siginit, 8\min(\|M_0\|, \rho))$
    \Else
      \State $D_{\text{root}}.\duplexing(\prfxroot \concat K \concat U \concat \siginit, 0)$
      \State $Z \gets \Call{Absorb}{D_{\text{root}}, A, \sigadmore, \sigadlast, 8\min(\|M_0\|, \rho)}$
    \EndIf
    \If{$n = 0$}
      \State $(C_0,\, T) \gets \Call{StreamEnc}{D_{\text{root}}, M_0, Z, \sigmsgmore, \sigmsglast, \tauroot}$
      \State \Return $C_0 \concat T$
    \EndIf
    \State $(C_0,\, \_) \gets \Call{StreamEnc}{D_{\text{root}}, M_0, Z, \sigmsgmore, \sigmsglast, 0}$
    \For{$j \gets 1$ \textbf{to} $n$ \textbf{in parallel}}
      \State $D_j \gets$ new $\Duplex$
      \State $Z_j \gets D_j.\duplexing(\prfxleaf \concat K \concat U \concat \langle j \rangle_8 \concat \siginit, 8\min(\|M_j\|, \rho))$
      \State $(C_j, T_j) \gets \Call{StreamEnc}{D_j, M_j, Z_j, \sigmsgmore, \sigmsglast, \tauleaf}$
    \EndFor
    \State $G \gets T_1 \concat \cdots \concat T_n$.
    \State $T \gets \Call{Absorb}{D_{\text{root}},\, G \concat \langle n \rangle_8,\, \sigaggmore,\, \sigagglast,\, \tauroot}$
    \State \Return $C_0 \concat C_1 \concat \cdots \concat C_n \concat T$
  \end{algorithmic}
\end{algorithm}

The initial keystream request for a message string $X$ is
$8\min(\|X\|, \rho)$, the bit length of its first duplex block. For the
root chunk $M_0$, that value is emitted by the closing \sigadlast call
when $A \neq \varepsilon$, and by the root \siginit call itself when
$A = \varepsilon$ and the associated data phase is elided. Each leaf's
\siginit call likewise emits $8\min(\|M_j\|, \rho)$ keystream bits for
the first duplex block of $M_j$, so the empty associated data root
\siginit call plays exactly the role a leaf \siginit call already plays.
When the corresponding message string is empty, the requested keystream
length is zero and the next message phase duplex call absorbs the empty
ciphertext duplex block carrying \sigmsglast. The final \sigmsglast call
in the root chunk requests
$\tauroot$ output bits when $n = 0$, namely the root tag $T$ emitted by
the elided-aggregation path, and zero output bits when $n \geq 1$
because the next duplex operation on the root is then the first
aggregation block; the corresponding call on a leaf requests $\tauleaf$
bits, namely the leaf tag. When $n \geq 1$ the final \sigagglast call
requests $\tauroot$ bits, which is the root tag $T$.

The leaf loop is annotated \textbf{in parallel} to make explicit that
the $n$ leaf computations are mutually independent; \Cref{sec:impl}
discusses the SIMD realizations. The annotation is an implementation
freedom, not a mode parameter: evaluating leaves serially, in SIMD
batches, or across cores leaves the transcript and wire format unchanged.

\paragraph{Streaming aggregation.}
The string $G = T_1 \concat \cdots \concat T_n$ in
\Cref{alg:enc,alg:dec} names the leaf tags only for specification. The
closing \Call{Absorb}{} consumes $G \concat \langle n \rangle_8$ as
$\rho$-byte duplex blocks in leaf order and advances the root state
after each, so an implementation need not hold $G$ in full. It can absorb
leaf tags in order as they become available, or buffer completed
out-of-order leaves until the next in-order tag or SIMD batch can be
absorbed, keeping only a bounded number of tags at a time. With
the bounded $1600$-bit state of every duplex, this keeps the working
memory constant in $\|M\|$ for a fixed degree of parallelism, growing
only with the number of leaves evaluated at once rather than with the
message length; \Cref{sec:impl} describes the batched realization.

\subsection{Decryption}
\label{sec:dec}

\Cref{alg:dec} specifies $\Dec_K(U, A, C \concat T)$. The procedure
mirrors $\Enc$ at the duplex block level: each ciphertext duplex block
$c_i$ is absorbed into the appropriate duplex (root or leaf) under the
corresponding \sigmsgmore or \sigmsglast suffix, and the plaintext duplex
block is recovered as $m_i = c_i \oplus Z^{(i)}$, writing $Z^{(i)}$ for
the value the running keystream variable $Z$ of \textsc{StreamDec} holds
when duplex block $i$ is processed ($i < t$ inside the loop, $i = t$ after
it), the same value the encryption procedure would have produced.
The procedure
absorbs ciphertext bytes before the final tag comparison, so the
verification transcript is determined by $(K, U, A, C)$ for every
in-domain ciphertext, accepting or not. This property is used by the
direct mu-ind proof to argue that encryption-first and
verification-first transcript classes are well defined regardless of the
tag-comparison outcome.

\begin{algorithm}[t]
  \caption{$\Dec_K(U, A, C \concat T)$.}
  \label{alg:dec}
  \begin{algorithmic}[1]
    \Require $K, U, A$ as in \Cref{alg:enc}, ciphertext $C$ with $\|C\| \leq M_{\max}$, candidate tag $T \in \bits^{\tauroot}$.
    \Ensure $M$ with $\|M\| = \|C\|$, or $\bot$.
    \State $C_0 \gets$ first $\min(\|C\|, \beta)$ bytes of $C$ (possibly $\varepsilon$).
    \State Partition the remaining suffix into chunks $C_1, \dots, C_n$ of exactly $\beta$ bytes each, except that the last chunk may be shorter but nonempty, so $n = \leaves(C)$.
    \State $D_{\text{root}} \gets$ new $\Duplex$
    \If{$A = \varepsilon$}
      \State $Z \gets D_{\text{root}}.\duplexing(\prfxroot \concat K \concat U \concat \siginit, 8\min(\|C_0\|, \rho))$
    \Else
      \State $D_{\text{root}}.\duplexing(\prfxroot \concat K \concat U \concat \siginit, 0)$
      \State $Z \gets \Call{Absorb}{D_{\text{root}}, A, \sigadmore, \sigadlast, 8\min(\|C_0\|, \rho)}$
    \EndIf
    \If{$n = 0$}
      \State $(M_0,\, T') \gets \Call{StreamDec}{D_{\text{root}}, C_0, Z, \sigmsgmore, \sigmsglast, \tauroot}$
      \State \Return $M_0$ if $T' = T$ (compared in constant time), else $\bot$.
    \EndIf
    \State $(M_0,\, \_) \gets \Call{StreamDec}{D_{\text{root}}, C_0, Z, \sigmsgmore, \sigmsglast, 0}$
    \For{$j \gets 1$ \textbf{to} $n$ \textbf{in parallel}}
      \State $D_j \gets$ new $\Duplex$
      \State $Z_j \gets D_j.\duplexing(\prfxleaf \concat K \concat U \concat \langle j \rangle_8 \concat \siginit, 8\min(\|C_j\|, \rho))$
      \State $(M_j, T_j) \gets \Call{StreamDec}{D_j, C_j, Z_j, \sigmsgmore, \sigmsglast, \tauleaf}$
    \EndFor
    \State $G \gets T_1 \concat \cdots \concat T_n$.
    \State $T' \gets \Call{Absorb}{D_{\text{root}},\, G \concat \langle n \rangle_8,\, \sigaggmore,\, \sigagglast,\, \tauroot}$
    \If{$T' = T$ (compared in constant time)}
      \State \Return $M_0 \concat M_1 \concat \cdots \concat M_n$
    \Else
      \State \Return $\bot$
    \EndIf
  \end{algorithmic}
\end{algorithm}

The $n = 0$ and empty-body cases mirror their encryption counterparts
(\Cref{sec:enc}): for $n = 0$ the aggregation phase is elided and the
closing \sigmsglast call of the root chunk emits the candidate tag $T'$
directly, and an empty body still performs the single empty \sigmsglast
call of \Cref{alg:helpers}, requesting $\tauroot$ output bits.

\paragraph{Correctness.}
For every $K \in \bits^k$, $U \in \bits^{\nu}$,
$A$ with $\|A\| \leq A_{\max}$, and $M$ with $\|M\| \leq M_{\max}$,
$\Dec_K(U, A, \Enc_K(U, A, M)) = M$. This follows by inspection: every
duplex call in $\Dec_K$ receives the same input as the corresponding
call in $\Enc_K$ (each ciphertext duplex block is absorbed under the same
phase tag in both directions), so the duplex states and the recomputed
root tag $T'$ exactly match. The constant-time comparison $T' = T$
succeeds, and the recovered $m_i = c_i \oplus Z^{(i)} = (m_i \oplus
Z^{(i)}) \oplus Z^{(i)} = m_i$ at every position.

\begin{lemma}[\TW{} tidiness]
\label{lem:tw-tidiness}
For every valid \TW{} decryption input, if
$\Dec_K(U, A, C \concat T) = M \neq \bot$, then
$\Enc_K(U, A, M) = C \concat T$.
\end{lemma}

\begin{proof}
An accepting decryption first passes the syntax and length checks of
\Cref{alg:dec}, so the recovered message $M$ has $\|M\| = \|C\|$ and the
same canonical chunking as the ciphertext body. The decryption transcript
absorbs $K$, $U$, $A$, and each ciphertext block under the same duplex
instances and phase suffixes used by encryption. Its stream outputs recover
each plaintext block as $M_i = C_i \oplus Z_i$, so re-encrypting the recovered
message under the same transcript emits $C_i = M_i \oplus Z_i$ and absorbs the
same ciphertext block at every message position. The leaf tags and final root
candidate tag recomputed by decryption are therefore exactly the values
recomputed by this re-encryption. Since decryption accepts only when its final
candidate tag equals the submitted tag $T$, re-encryption returns the submitted
body and tag $C \concat T$.
\end{proof}
