¥section{Concrete Security Summary}
¥label{sec:concrete-security}

¥Cref{sec:aead-security,sec:root-tag-hash-security} separate the security
analysis into AEAD bounds and root tag hash and committing bounds. This section
instantiates those bounds at the
implemented ¥TW{} parameters and records the single concrete work cap used
throughout the paper.

¥subsection{Concrete TW128 Bounds}
¥label{sec:concrete}

The implemented parameters of ¥Cref{sec:params} fix
¥[
  k = c = ¥nu = ¥tauroot = ¥tauleaf = 256.
¥]
Substituting into
¥Cref{cor:ae,thm:mu-ind,thm:int-rup,thm:coll,thm:pre,cor:second-preimage-rs04,cor:cmtds4,thm:epre}
gives the following closed-form bounds.

¥paragraph{All-in-one AE.}
¥[
  ¥Advae_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥Nprim(¥Nprim + 1)}{2^{257}}
  + ¥frac{¥Nprim + ¥Qv + ¥Nleaf}{2^{256}}.
¥]

¥paragraph{Multi-user indistinguishability.}
¥[
  ¥Advmuind_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥Nprim(¥Nprim + 1)}{2^{257}}
  + ¥frac{D ¥Nprim + ¥Qv + ¥Nleaf}{2^{256}}
  + ¥frac{D(D - 1)}{2^{257}}.
¥]

¥paragraph{¥textsf{INT-RUP} integrity.}
¥[
  ¥AdvintRUP_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥Nprim + ¥Qv + ¥Nleaf}{2^{256}}.
¥]

¥paragraph{$s$-way collision resistance of $¥HTW$.}
For every $s ¥geq 2$,
¥[
  ¥AdvColl_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥binom{¥Nprim+¥Nleaf}{2}}{2^{256}}
  + ¥frac{¥binom{¥Nprim + s}{s}}{2^{256 (s - 1)}}.
¥]
For $s=2$, this is the ordinary two-input collision bound:
¥[
¥begin{aligned}
  ¥AdvColl_¥TW(¥mathcal{A})
¥leq¥;&
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{(¥Nprim+¥Nleaf)(¥Nprim+¥Nleaf-1)}{2^{257}} ¥¥
& + ¥frac{(¥Nprim + 1)(¥Nprim + 2)}{2^{257}} .
¥end{aligned}
¥]

¥paragraph{Second-preimage resistance of $¥HTW$.}
By ¥Cref{cor:second-preimage-rs04}, the standard and everywhere
¥cite{RS04} second-preimage advantages of $¥HTW$ are bounded by the same
$s=2$ collision expression above.

¥paragraph{Preimage resistance of $¥HTW$.}
For fixed byte lengths $a,¥mu$, let
$m_{a,¥mu}=k+¥nu+8a+8¥mu$. By ¥Cref{thm:pre},
¥[
¥begin{aligned}
  ¥AdvPreSlice{a}{¥mu}_¥TW(¥mathcal{A})
¥leq¥;&
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{(¥Nprim+¥Nleaf)(¥Nprim+¥Nleaf-1)}{2^{257}} ¥¥
& + ¥frac{¥Nprim + 1}{2^{256}}
  + 2^{256 - m_{a,¥mu}} .
¥end{aligned}
¥]
Under the implemented parameters $k = ¥nu = 256$, the slice term is
$2^{-256-8a-8¥mu}$.

¥paragraph{$s$-way CMTDs-4 committing security.}
For every $s ¥geq 2$, the all-bodies-equal special case drops the
known-key leaf tag collision term:
¥[
  ¥Advcmtds{4}_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥binom{¥Nprim + s}{s}}{2^{256 (s - 1)}}.
¥]

¥begin{remark}[Two-Opening CMTDs-4 Specialization]
¥label{rem:cmtd4-s2}
Setting $s = 2$ recovers the ordinary two-opening
CMTDs-4 statement of ¥cite{BH22}:
¥[
  ¥Advcmtds{4}_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥binom{¥Nprim + 2}{2}}{2^{256}}
  ¥;=¥;
  ¥frac{¥Ntot(¥Ntot + 1) + (¥Nprim + 1)(¥Nprim + 2)}{2^{257}}.
¥]
¥end{remark}

¥paragraph{Everywhere preimage resistance of $¥HTW$.}
¥[
  ¥AdvePre_¥TW(¥mathcal{A})
  ¥;¥leq¥;
  ¥frac{¥Ntot(¥Ntot + 1)}{2^{257}}
  + ¥frac{¥Nprim + 1}{2^{256}}.
¥]

¥subsection{Concrete Security Claim}
¥label{sec:concrete-claim}

¥begin{corollary}[Concrete ¥TW{} Security]
¥label{cor:concrete-security}
Under the implemented parameters $k = c = ¥nu = ¥tauroot = ¥tauleaf = 256$, every
adversary with work cap $¥Ntot ¥leq 2^{63}$---and, in the multi-user case,
user cap $D ¥leq 2^{63}$---has advantage at most $2^{-128}$ in each of
¥TW{}'s notions: multi-user indistinguishability (¥Cref{thm:mu-ind}),
all-in-one AE (¥Cref{cor:ae}), ¥textsf{INT-RUP} integrity
(¥Cref{thm:int-rup}), the hash security of
$¥HTW$---$s$-way collision resistance for every $s ¥geq 2$ in the sense
of ¥cite{BH22}, with the ¥cite{RS04} notions of standard and everywhere
second-preimage resistance inherited from collision resistance on every
fixed input slice, standard preimage resistance on every fixed input
slice, and everywhere preimage resistance
(¥Cref{thm:coll,cor:second-preimage-rs04,thm:pre,thm:epre})---and the ¥cite{BH22}
CMTDs-4 committing bound it yields (¥Cref{cor:cmtds4}).
¥end{corollary}

¥begin{proof}
The resource consequences of ¥Cref{sec:resources} give
$¥Nprim ¥leq ¥Ntot$, $¥Qv ¥leq ¥Ntot$, $¥Nleaf ¥leq ¥Ntot$, and
$¥Nprim+¥Nleaf ¥leq ¥Ntot$. The user cap $D$ remains independent, since
created-but-idle users need not contribute to $N$.

At $¥Ntot ¥leq 2^{63}$, each flat-sponge term---at $¥Ntot$ or at
$¥Nprim$---and each birthday-scale root or leaf term at $s=2$ is at most
$2^{-131} + 2^{-192}$, while each
linear root-preimage, key-guessing, verification, or leaf tag term with no
factor $D$ is at most a $2^{-193}$-scale term.
The fixed-slice Pre degradation is at most $2^{-256}$, since
$m_{a,¥mu} ¥geq k+¥nu = 512$.
Thus the largest non-multi-user bound is the $s=2$ collision bound, which is below
$4 ¥cdot 2^{-131} = 2^{-129}$; larger $s$ only decreases the
root-collision term. The all-in-one AE bound carries its two flat-sponge
terms as its only birthday-scale terms and lies below $2^{-129}$, and the
¥textsf{INT-RUP} bound carries $¥Lift_c(¥Ntot)$ alone. In the multi-user
case, using $D ¥leq 2^{63}$,
¥[
  ¥Advmuind_¥TW(¥mathcal{A})
  < ¥bigl(2^{-130} + 2^{-193}¥bigr) + 2^{-130} + 2^{-192} + 2^{-131}
  < 2^{-128}:
¥]
the two flat-sponge terms sum to at most
$2 ¥cdot (2^{-131} + 2^{-194}) = 2^{-130} + 2^{-193}$, the key-guessing
term satisfies $D ¥Nprim / 2^{256} ¥leq 2^{126}/2^{256} = 2^{-130}$, the
remaining linear terms satisfy
$(¥Qv + ¥Nleaf)/2^{256} ¥leq 2^{64}/2^{256} = 2^{-192}$, and
$D(D-1)/2^{257} < 2^{-131}$; the total is below
$5 ¥cdot 2^{-131} + 2^{-192} + 2^{-193} < 2^{-128}$. These estimates
instantiate every closed form in ¥Cref{sec:concrete};
¥Cref{sec:bound-discussion} examines the margin they leave.
¥end{proof}

¥begin{table}[t]
¥centering
¥caption{Concrete ¥TW{} security at the work cap $¥Ntot ¥leq 2^{63}$
(with $D ¥leq 2^{63}$ for mu-ind), under
$k = c = ¥nu = ¥tauroot = ¥tauleaf = 256$ and the resource consequences
$¥Nprim, ¥Qv, ¥Nleaf ¥leq ¥Ntot$ and $¥Nprim + ¥Nleaf ¥leq ¥Ntot$ of
¥Cref{sec:resources}. The Coll and
CMTDs-4 rows hold for every $s ¥geq 2$; larger $s$ only shrinks the
root-collision term.}
¥label{tab:concrete-security}
¥begin{tabular}{@{}lcc@{}}
¥toprule
Notion & Dominant scale & At the cap ¥¥
¥midrule
All-in-one AE & $¥Lift_c$ & $¥leq 2^{-128}$ ¥¥
Multi-user ind. & $D¥,¥KeyGuess_k(¥Nprim)$ & $¥leq 2^{-128}$ ¥¥
¥textsf{INT-RUP} & $¥Lift_c$ & $¥leq 2^{-128}$ ¥¥
$¥HTW$ collision (Coll) & $¥Lift_c$, $¥LeafColl$, $¥RootColl$ & $¥leq 2^{-128}$ ¥¥
$¥HTW$ second-preimage (Sec/eSec) & inherited from Coll & $¥leq 2^{-128}$ ¥¥
$¥HTW$ preimage (Pre) & $¥Lift_c$, $¥LeafColl$ & $¥leq 2^{-128}$ ¥¥
$¥HTW$ everywhere preimage (ePre) & $¥Lift_c$ & $¥leq 2^{-128}$ ¥¥
CMTDs-4 ¥cite{BH22} & $¥Lift_c$ and $¥RootColl$ & $¥leq 2^{-128}$ ¥¥
¥bottomrule
¥end{tabular}
¥end{table}

¥subsection{Discussion of the Bounds}
¥label{sec:bound-discussion}

The bounds of ¥Cref{sec:concrete} aggregate the loss terms of
¥Cref{sec:loss-terms}, whose sizes at the work cap
¥Cref{tab:concrete-security} records and whose dominance
¥Cref{sec:concrete-claim} proves.

¥paragraph{At the concrete cap.}
At $¥Ntot ¥leq 2^{63}$, the hash bounds other than ePre and the
CMTDs-4 bound have flat-sponge
and root or leaf birthday terms on the same $2^{-131}$ scale; the
ePre and ¥textsf{INT-RUP} bounds retain the flat sponge loss
as their only birthday-scale term, and the single-user AE bound carries
its two flat-sponge terms, at $¥Ntot$ and $¥Nprim$, as its only
birthday-scale terms. Thus the flat sponge loss is not always the largest
summand: under the loose per-term cap, the $s=2$ root-collision term
$¥binom{¥Nprim+2}{2}/2^{256}$ is on the same scale as $¥Lift_c(¥Ntot)$.
The multi-user bound is the exception: its
hybrid-induced
term $D¥,¥KeyGuess_k(¥Nprim)$ can reach $2^{-130}$ at the extreme cap
$D=¥Nprim=2^{63}$. That corner is a property of the bound, not of any
admissible attack: the matching attack of the Tightness paragraph below
needs one accepted nonempty encryption per targeted user, and even the
empty-AD one-block case costs two duplex calls (root initialization and
closing root message). With $t$ targeted users and $q=¥Nprim$ direct
guesses, the joint cap imposes $2t+q ¥leq 2^{63}$, so the feasible
key-guessing attack scale is about $2^{-133}$, reached near
$t=2^{61}$ and $q=2^{62}$. The remaining factor is hybrid slack from
charging created-but-idle users. Expressed in bytes, $¥Ntot ¥leq 2^{63}$ corresponds to
at most $¥rho ¥cdot 2^{63} = 167 ¥cdot 2^{63} < 2^{71}$ bytes of
plaintext, associated data, ciphertext, and aggregation through the
duplex (¥Cref{sec:params}).

¥paragraph{Margin at the cap.}
¥Cref{cor:concrete-security} clears its target with a stated remainder:
at the joint corner $D = ¥Nprim = 2^{63}$ the multi-user estimate has
exact value $5 ¥cdot 2^{-131} + 2^{-194}$, since the corner forces
$N=0$ and hence $¥Qv=¥Nleaf=0$; this is just over five eighths of the
$2^{-128}$ budget. The largest of the remaining bounds, the $s = 2$
collision bound, stays below $4 ¥cdot 2^{-131}$
(¥Cref{sec:concrete-claim}). The closeness at the corner is a proof
artifact rather than a consequence of the design. The corner itself is
unoccupiable: it forces $N = 0$, as the previous paragraph records, and
an adversary without construction computations receives identical
answers in both worlds---the primitive interface is the same real
permutation (¥Cref{sec:games-pp})---so its advantage there is exactly
$0$. At resource splits an adversary can occupy, the multi-user
key-guessing witness reaches about the $2^{-133}$ scale, while the
root-collision and flat-sponge tightness witnesses can still reach the
$2^{-131}$ scale. The intervening distance to the proof bound is
consumed by the two flat-sponge composition terms and the hybrid slack
recorded above, the overhead of the indifferentiability route. The margin also widens away
from the corner: at $D ¥leq 2^{32}$, the $D$-indexed terms drop below
$2^{-160}$ and the multi-user bound falls to its two flat-sponge terms,
below $2^{-130} + 2^{-159}$, two bits under the target. A direct
keyed-duplex analysis would be expected to replace the quadratic
$¥Lift_c$ terms by finer construction--primitive cross terms, much as
the keyed-duplex bounds synthesized by ¥cite{Men23} improve on the
sponge-indifferentiability bound underlying the original SpongeWrap
analysis of ¥cite{BDPV11}; ¥Cref{sec:limitations} discusses that route
and the gaps it would need to close.

¥paragraph{Reading the work cap.}
¥Cref{cor:concrete-security} is a success-probability statement at a fixed
cap, not a statement that security is exhausted there. The closed forms of
¥Cref{sec:concrete} remain explicit functions of the resources beyond
$2^{63}$, and their dominant terms are birthday-type in $¥Ntot$ on the
$256$-bit capacity, so the guarantees degrade quadratically rather than
abruptly: at $¥Ntot = 2^{100}$, for example, the $s = 2$ collision bound is
still below $2^{-55}$. The bounds become vacuous only as $¥Ntot$ approaches
$2^{c/2} = 2^{128}$, where $¥Lift_c(¥Ntot)$ exceeds $1/2$
(¥Cref{sec:loss-terms}). The cap $¥Ntot ¥leq 2^{63}$ is therefore a
data-scale choice: a single work bound at which every notion's advantage
lies below the $2^{-128}$ target simultaneously, not the largest workload
the mode tolerates.

¥paragraph{Tightness.}
¥begin{itemize}
¥item ¥emph{$¥KeyGuess_k(Q) = Q / 2^k$.} Tight at constants: a direct
  random-guess attack on a $k$-bit key matches the per-query success
  probability $1 / 2^k$. The multi-user bound's dominant term
  $D¥,¥KeyGuess_k(¥Nprim) = D¥Nprim / 2^k$ is likewise tight at the
  leading constant in the theorem's free-parameter setting, using the
  per-user nonce discipline of ¥Cref{sec:mu-ind}, which permits one
  nonce value across users. The adversary queries every targeted user
  on the same nonce $U$, empty associated data, and a known nonempty
  message---construction work charged to $N$, which does not enter the
  term---so each user's first ciphertext block reveals the keystream
  emitted by that user's root initialization call
  (¥Cref{tab:transcript-schedule}). Each direct guess is then a single
  forward primitive query at the root initialization transcript
  $¥prfxroot ¥concat K' ¥concat U$ for a fresh candidate key $K'$,
  whose output is compared against all $D$ collected keystream blocks
  at once; it matches some targeted key with probability $D / 2^k$, so
  $¥Nprim$ guesses recover a user key---and distinguish---with
  probability $¥approx D¥Nprim / 2^k$, matching the bound. Under the
  joint cap the construction work for those target encryptions lowers
  the feasible scale to about $2^{-133}$, as noted in the concrete-cap
  paragraph above.
¥item ¥emph{$¥RootColl_¥tau(Q, s) = ¥binom{Q + s}{s} / 2^{¥tau (s -
  1)}$.} Tight up to lower-order terms: it is the standard $s$-way
  multi-collision bound on a $¥tau$-bit projection of $¥ROflat$, and
  a generic birthday-style adversary against the random oracle
  matches the leading-order term. It is the root term of the collision
  bound ($¥HTW$ Coll, ¥Cref{thm:coll}). Its $¥Nprim$ counts every
  primitive query, though by Output-Point Separation
  (¥Cref{cor:output-sep}) only those whose induced $¥ROflat$ call lands at
  a root tag output point ($¥Rtag$, or $¥Rmsg^+$ for single-chunk
  ciphertexts) can enter the candidate sequence; a class-filtered count
  would be no larger, and potentially smaller, but the displayed bound keeps the
  $¥Nprim$ form for uniformity with ¥Cref{cor:ae,thm:mu-ind}, the birthday
  threshold at $¥tauroot = 256$ being unaffected.
¥item ¥emph{$¥RootPre_¥tau(Q) = (Q + 1) / 2^¥tau$.} Tight at constants: a
  generic preimage search against a fixed $¥tau$-bit target matches the
  per-query $2^{-¥tau}$ rate. It is the root term of the standard and
  everywhere preimage bounds, where a single target tag yields a linear term.
¥item ¥emph{Leaf tag term $¥Nleaf / 2^{¥tauleaf}$.} Tight at constants
  by a nonce-respecting attack: encrypt a single two-chunk message
  under nonce $U$, obtaining ciphertext with one leaf chunk and root
  tag $T$, then submit non-replay verification queries that each
  replace the leaf chunk by fresh bytes of the same length, keeping
  $T$. Each query recomputes the leaf tag at the hidden slot
  $(K, U, 1)$ and accepts whenever that fresh tag equals the
  encryption's hidden leaf tag $T_1$, since the aggregation
  string---and hence the recomputed root tag---is then unchanged. Each
  verification-side final leaf transcript therefore forges with
  probability $2^{-¥tauleaf}$, matching the bound's per-transcript
  rate.
¥item ¥emph{Known-key leaf collision $¥LeafColl_¥tau(Q)$.} Genuinely
  birthday-tight: when keys are adversary-supplied, direct queries can
  target leaf tag points, and a birthday search over chosen leaf bodies
  yields two distinct $¥HTW$ inputs sharing a leaf tag and hence
  colliding openings; the collision proof uses $Q=¥Nprim+¥Nleaf$.
¥item ¥emph{Flat sponge lift.} The term
  $¥Lift_c(¥Ntot) = ¥Ntot(¥Ntot + 1) / 2^{c + 1}$ dominates the
  random-permutation differentiating bound $f_P(¥Ntot)$ of
  ¥cite[Lemma‾5]{BDPV08} via ¥Cref{lem:lift-bound}. The
  differentiating bound $f_P(¥Ntot)$ is itself matched at leading order
  by the standard inner-collision differentiator, which succeeds
  against every simulator because the ideal-world construction
  interface is the random oracle regardless of simulator strategy; any
  residual conservatism in $¥Lift_c(¥Ntot)$ lies in composing
  indifferentiability into the specific keyed games, not in an
  improvable simulator bound, and is not specific to ¥TW{}. The
  real-vs-ideal games pay the same differentiating bound once more, at
  $¥Nprim$, to exchange the ideal-side simulator for the real
  permutation (¥Cref{lem:sim-perm-proximity}); since
  $¥Nprim ¥leq ¥Ntot$, that term never dominates the $¥Ntot$ term.
¥end{itemize}

Cross-scheme bound-level comparisons against prior sponge AEADs and
the committing AEAD line of ¥cite{BH22} are deferred to
¥Cref{sec:compare-table,sec:compare-sponge,sec:compare-commit}.
