\section{Committing Security and Context Discoverability}
\label{sec:cmtds3}

This section proves the random-oracle CMTDs-3 bound that the headline
CMTDs-4 statement (\Cref{thm:cmtds4}) consumes via the trivial
promotion of \Cref{app:committing-transfer}. The public-permutation
CMTDs-3 statement follows by the flat-sponge lift of
\Cref{app:flat-sponge-lift}. The same root tag argument, with the
$s$-way collision replaced by a preimage to a fixed target tag, gives
the random-oracle context-discoverability bound
(\Cref{thm:cdy-ro}) underlying the headline CDY statement
(\Cref{thm:cdy}). Finally, the tag-projected CMTDs-4 bound
(\Cref{thm:tag-cmtds4-ro}) keeps the same root tag collision argument
but adds a known-key leaf tag collision term, because compact openings
may use different ciphertext bodies under one common tag.

\begin{theorem}[Random-Oracle CMTDs-3]
\label{thm:cmtds3-ro}
For every $s \geq 2$ and every $s$-way CMTDs-3
adversary $\mathcal{B}$ in the \TW{} random-oracle model
(\Cref{sec:ro-model}),
\[
  \Advcmtds{3}_\RO(\mathcal{B})
  \;\leq\; \RootColl_{\tauroot}(\qRO(\mathcal{B}), s)
  = \frac{\binom{\qRO(\mathcal{B}) + s}{s}}{2^{\tauroot (s - 1)}}.
\]
\end{theorem}

\begin{proof}
Unlike the privacy and INT-CTXT proofs, the CMTDs-3 analysis has no
$\badkey$ event: all $s$ keys are
adversary-supplied, so a direct query to a keyed transcript is one of
$\mathcal{B}$'s visible $\ROflat$ queries and is counted in
$\qRO(\mathcal{B})$.

Run the random-oracle CMTDs-3 game (\Cref{sec:ro-model}) and define a
candidate sequence for every execution. During $\mathcal{B}$'s direct
oracle phase, when $\mathcal{B}$ makes a direct query to an input $Y$
that is not already in the sequence, append $Y$ immediately before
answering the query if $\KeyedTWOut(Y)$ decodes to a root tag
output-point class, namely $\Rmsg^+$ (the single-chunk root tag, with
the aggregation phase elided when $n = 0$) or $\Rtag$ (the multi-chunk
root tag). This predicate depends on $Y$ alone through the exact decoder
of \Cref{lem:bridge-decode}, which ignores the requested output length,
so both the decision to append and the string $Y$ are determined before
the query's $\ROflat$ lookup. By Output-Point Separation
(\Cref{cor:output-sep}) each input decodes to at most one output-point
class, so each distinct direct query contributes at most one candidate.
Since there is no construction oracle before $\mathcal{B}$ outputs its
tuples, each direct-query candidate is first touched at its append step.

After $\mathcal{B}$ outputs $C \concat T$ and tuples
$(K_i,N_i,A_i,M_i)_{i=1}^s$, stop appending challenger candidates if
the syntax, message-length, or pairwise-distinct-triple check fails.
Otherwise, as the
challenger evaluates the $s$ deterministic decryption checks, let
$R_i$ be the final root transcript reached by
$\Dec_{K_i}^\RO(N_i,A_i,C \concat T)$ in check $i$, and append
$\flatmap(R_i)$ immediately before the root tag oracle answer is
sampled, unless that input is already in the sequence. If a challenger
input was already touched by a direct query, then
\Cref{lem:bridge-decode} and Output-Point Separation
(\Cref{cor:output-sep}) imply that the earlier query was a final-root
candidate and the input is already in the sequence. Otherwise,
\Cref{cor:output-sep} excludes all earlier challenger lookups outside
the final-root class, and Opening Triple Separation
(\Cref{cor:triple-sep}) excludes earlier final-root lookups from the
other checked triples. Thus no earlier lookup of any kind has touched
a newly appended candidate's input. The sequence therefore satisfies
the predictability and unrevealed-value premises of Adaptive Candidate
Collision (\Cref{lem:adaptive-candidate-collision}), and its length is
at most $\qRO(\mathcal{B}) + s$.

On a winning execution, the challenger has accepted the syntax,
message-length, and pairwise-distinct-triple checks, so the tuples are
valid and the $(K_i,N_i,A_i)$ triples are pairwise distinct. By
\Cref{cor:triple-sep}, the bridged final-root inputs
\[
  \flatmap(R_1),\dots,\flatmap(R_s)
\]
are pairwise distinct. Thus leaf tag collisions cannot merge the root
inputs relevant to a CMTDs-3 win. Since every decryption check
accepts, the
$\tauroot$-bit projections at the $s$ distinct challenger final-root
inputs all equal the supplied tag $T$:
\[
  \bigl\lfloor\ROflat(\flatmap(R_1))\bigr\rfloor_{\tauroot}
  =
  \cdots
  =
  \bigl\lfloor\ROflat(\flatmap(R_s))\bigr\rfloor_{\tauroot}
  =
  T .
\]
Hence the win event is contained in the $s$-way candidate-collision
event. Applying \Cref{lem:adaptive-candidate-collision} with
$Q=\qRO(\mathcal{B})$ and $\tau=\tauroot$ gives
\[
  \Advcmtds{3}_\RO(\mathcal{B})
  \leq
  \binom{\qRO(\mathcal{B}) + s}{s} \cdot 2^{-\tauroot(s-1)}
  =
  \RootColl_{\tauroot}(\qRO(\mathcal{B}), s).
\]
\end{proof}

\begin{lemma}[Random-Oracle Known-Key Leaf Collision]
\label{lem:known-key-leaf-collision}
For every tag-CMTDs-4 adversary $\mathcal{B}$ in the \TW{} random-oracle
model, let $\badleaf^\star$ be the event that two distinct final leaf
transcripts generated by the tag-CMTDs-4 challenger decryption checks
receive the same $\tauleaf$-bit $\RF$ projection. Then
\[
  \Pr[\badleaf^\star]
  \leq
  \LeafColl_{\tauleaf}(\qRO(\mathcal{B})+\nleaf(\mathcal{B}))
  =
  \frac{\binom{\qRO(\mathcal{B})+\nleaf(\mathcal{B})}{2}}{2^{\tauleaf}}.
\]
\end{lemma}

\begin{proof}
Build a leaf tag candidate sequence for the tag-CMTDs-4 game. During
$\mathcal{B}$'s direct oracle phase, append each distinct direct query
input $Y$ before answering it if $\KeyedTWOut(Y)$ decodes to a final
leaf tag output-point class $\Ltag[j]$. After $\mathcal{B}$ outputs its
common tag and opening tuples, as the challenger performs its
deterministic decryption checks, append the bridged input of each newly
created distinct final leaf transcript immediately before the leaf tag
oracle answer is sampled, unless that input is already in the sequence.
If the input was touched earlier by a direct query, then
\Cref{lem:bridge-decode} and \Cref{cor:output-sep} imply that the
earlier query was already appended as a leaf tag candidate. If it was
touched earlier by a construction computation, then
\Cref{cor:output-sep}, transcript injectivity
(\Cref{lem:transcript-inj}), and bridge injectivity imply that the same
final leaf transcript had already been generated; repeated evaluations
are not new collision opportunities. Thus every newly appended
candidate satisfies the predictability and unrevealed-value premises of
the adaptive candidate-collision argument, and the sequence length is at
most $\qRO(\mathcal{B})+\nleaf(\mathcal{B})$.

For any fixed unordered pair of candidate positions, expose the two
positions in chronological order. When the later candidate is appended,
its $\tauleaf$-bit projection is still unrevealed and uniform
independently of the earlier one, so the pair collides with probability
$2^{-\tauleaf}$. A union bound over at most
$\binom{\qRO(\mathcal{B})+\nleaf(\mathcal{B})}{2}$ pairs gives the
claim. The event $\badleaf^\star$ is contained in this candidate
collision event because every construction-generated final leaf
transcript is either appended when first created or was already appended
by a direct query to the same bridged input.
\end{proof}

\begin{theorem}[Random-Oracle Tag-CMTDs-4]
\label{thm:tag-cmtds4-ro}
For every $s \geq 2$ and every $s$-way tag-CMTDs-4
adversary $\mathcal{B}$ in the \TW{} random-oracle model,
\[
  \Advtagcmtds{4}_{\RO}(\mathcal{B})
  \;\leq\;
  \LeafColl_{\tauleaf}(\qRO(\mathcal{B})+\nleaf(\mathcal{B}))
  + \RootColl_{\tauroot}(\qRO(\mathcal{B}), s).
\]
\end{theorem}

\begin{proof}
Run the random-oracle tag-CMTDs-4 game. By
\Cref{lem:known-key-leaf-collision}, the probability of
$\badleaf^\star$ is at most the stated leaf-collision term, so it
remains to bound the winning probability conditioned on
$\neg\badleaf^\star$.

Build the root tag candidate sequence exactly as in
\Cref{thm:cmtds3-ro}'s direct-oracle phase: each distinct direct query
whose input decodes to a root tag output-point class ($\Rmsg^+$ or
$\Rtag$) is appended before its $\ROflat$ lookup. After
$\mathcal{B}$ outputs
\[
  \bigl(T,(C_i,K_i,N_i,A_i,M_i)_{i=1}^s\bigr),
\]
stop appending challenger candidates if any syntax, message-length, or
pairwise-full-input check fails. Otherwise, as the challenger evaluates
the $s$ deterministic decryption checks, let $R_i$ be the final root
transcript reached by
$\Dec_{K_i}^{\RO}(N_i,A_i,C_i \concat T)$ in check $i$, and append
$\flatmap(R_i)$ immediately before the root tag oracle answer is
sampled, unless that input is already in the sequence. If a challenger
input was already touched by a direct query, then
\Cref{lem:bridge-decode} and \Cref{cor:output-sep} imply that the
earlier query was a final-root candidate and the input is already in
the sequence. Otherwise, \Cref{cor:output-sep} excludes earlier
challenger lookups outside the final-root class; earlier final-root
lookups either have a different address or have already caused this
address to be appended. Thus newly appended root candidates satisfy the
predictability and unrevealed-value premises of
\Cref{lem:adaptive-candidate-collision}, and the sequence length is at
most $\qRO(\mathcal{B})+s$.

On a winning execution with $\neg\badleaf^\star$, the full tuples
$(K_i,N_i,A_i,M_i)$ are pairwise distinct and all decryption checks
accept under the common tag $T$. We first show that the bridged final
root inputs $\flatmap(R_1),\dots,\flatmap(R_s)$ are pairwise distinct.
Suppose instead that checks $i \neq j$ reach the same final root input.
The bridge and transcript encodings are injective, so the root
transcripts have the same key, nonce, associated data, root ciphertext
chunk, root tag output point, and, when leaves are present, the same
ordered leaf tag aggregation string. The trailing encoded leaf count
gives the same number of leaves. For each leaf position, equality of the
aggregated leaf tag values together with $\neg\badleaf^\star$ implies
that the two final leaf transcripts are the same; hence the
corresponding ciphertext leaf chunks are the same. Thus the two
decryption checks use the same $(K,N,A,C\concat T)$. Determinism of
$\Dec{}$ gives the same plaintext, so
$(K_i,N_i,A_i,M_i)=(K_j,N_j,A_j,M_j)$, contradicting the tag-CMTDs-4
pairwise-full-input check. The final root inputs are therefore
pairwise distinct.

Since every decryption check accepts, the $\tauroot$-bit projections at
these $s$ distinct final-root candidates all equal the supplied tag
$T$. The win event under $\neg\badleaf^\star$ is contained in the
$s$-way root candidate-collision event, which
\Cref{lem:adaptive-candidate-collision} bounds by
$\RootColl_{\tauroot}(\qRO(\mathcal{B}),s)$. Adding the
$\badleaf^\star$ probability gives the theorem.
\end{proof}

\begin{theorem}[Random-Oracle CDY]
\label{thm:cdy-ro}
For every query-independent target tag $T^* \in \bits^{\tauroot}$ and
every context-discoverability adversary $\mathcal{B}$ in the \TW{}
random-oracle model (\Cref{sec:ro-model}),
\[
  \Advcdy_\RO(\mathcal{B})
  \;\leq\; \RootPre_{\tauroot}(\qRO(\mathcal{B}))
  = \frac{\qRO(\mathcal{B}) + 1}{2^{\tauroot}}.
\]
\end{theorem}

\begin{proof}
As in \Cref{thm:cmtds3-ro}, the CDY analysis has no $\badkey$ event:
the single key is adversary-supplied, so a direct query to a keyed
transcript is one of $\mathcal{B}$'s visible $\ROflat$ queries and is
counted in $\qRO(\mathcal{B})$. Fix the query-independent target
$T^*$, which is therefore independent of $\ROflat$.

Run the random-oracle CDY game (\Cref{sec:ro-model}) and build the
root tag candidate sequence exactly as in the direct-oracle phase of
\Cref{thm:cmtds3-ro}: each distinct direct query whose input decodes to
a root tag output-point class ($\Rmsg^+$ or $\Rtag$) is appended before
its $\ROflat$ lookup and first touched at its append step.

After $\mathcal{B}$ outputs the ciphertext body $C$ and the single
context $(K,N,A)$, stop appending if the syntax or ciphertext-validity
precheck on $C \concat T^*$ fails. Otherwise let $R$ be the final root
transcript reached by the one deterministic decryption check
$\Dec_{K}^\RO(N,A,C \concat T^*)$, and append $\flatmap(R)$ immediately
before its root tag oracle answer is sampled, unless that input is
already in the sequence. If $\flatmap(R)$ was already touched by a
direct query, then \Cref{lem:bridge-decode} and Output-Point Separation
(\Cref{cor:output-sep}) imply the earlier query was a final-root
candidate and the input is already in the sequence; otherwise
\Cref{cor:output-sep} excludes all earlier challenger lookups outside
the final-root class. Unlike \Cref{thm:cmtds3-ro}, there is a single
context, so no appeal to Opening Triple Separation
(\Cref{cor:triple-sep}) is needed: no pairwise distinctness among
final-root inputs is required. Thus no earlier lookup of any kind has
touched the newly appended candidate's input. The sequence therefore
satisfies the predictability and unrevealed-value premises of Adaptive
Candidate Preimage (\Cref{lem:adaptive-candidate-preimage}), and its
length is at most $\qRO(\mathcal{B}) + 1$.

On a winning execution the precheck passes and the single decryption
check accepts. By \Cref{alg:dec}, acceptance is the constant-time
equality $T' = T^*$, where $T'$ is the $\tauroot$-bit projection at the
final root transcript $R$; in the random-oracle model
$T' = \bigl\lfloor \ROflat(\flatmap(R)) \bigr\rfloor_{\tauroot}$. Hence
the win event is contained in the event that some candidate's
$\tauroot$-bit projection equals the fixed target $T^*$. Applying
\Cref{lem:adaptive-candidate-preimage} with $Q = \qRO(\mathcal{B})$,
$\tau = \tauroot$, and $t = T^*$ gives
\[
  \Advcdy_\RO(\mathcal{B})
  \leq
  (\qRO(\mathcal{B}) + 1) \cdot 2^{-\tauroot}
  =
  \RootPre_{\tauroot}(\qRO(\mathcal{B})).
\]
\end{proof}
