\section{Performance Evaluation}
\label{sec:performance}

\subsection{Optimized Implementations}
\label{sec:impl}

We analyze a Go implementation of \TW{}\footnote{The implementation is available
at \url{https://github.com/codahale/treewrap}.} with optimized assembly paths
for the performance-critical permutation and absorb/squeeze loops. We
compare three vectorized assembly paths: \texttt{amd64} AVX-512,
\texttt{amd64} AVX2, and \texttt{arm64} NEON using the Armv8.2 SHA-3
extension. The framing, domain separation, padding, tree bookkeeping, and
dispatch remain in shared Go code. A pure Go path uses a scalar permutation
and a scalar eight-instance loop, and serves both as a correctness oracle for
the assembly cores and as a constant-time fallback on other architectures.

The tree structure of \TW{} exposes two distinct permutation workloads. The
root duplex---which absorbs the associated data, processes chunk~$0$, and
absorbs the leaf tag aggregation transcript---is inherently sequential, since
each call consumes the previous call's output. It is driven by a
\emph{single-duplex} ($\times 1$) core, except for its chunk-$0$ message phase.
The leaf duplexes operate on disjoint state and disjoint inputs
(\Cref{sec:tw128}), so complete leaf chunks are batched and run through an
\emph{eight-way} ($\times 8$) core. Leftover runs of two to seven complete
chunks use narrower remainder kernels, while a single leftover complete chunk,
a partial trailing chunk, and the count-aggregation tail fall back to the
single-duplex core.

Chunk~$0$ itself runs on the batched kernels rather than serially, a technique
we refer to as \emph{chunk~$0$ fusion}. The root duplex's chunk-$0$ message phase
has the same kernel-visible schedule as a leaf chunk and differs only in its
initial state. The implementation therefore seeds lane~$0$ of the first batched
call with the root state, runs chunk~$0$ alongside the first leaf chunks, then
writes lane~$0$'s output state back to the root duplex before the root absorbs
the leaf tags from that same call. This avoids a serial pass over chunk~$0$ and
is the reason the throughput curve drops as soon as complete leaves are present
(\Cref{sec:throughput}). \Cref{app:kernels} gives the lane-major layout,
remainder-kernel strategies, lane~$0$ writeback details, and instruction-level
kernel structure.

\paragraph{Architecture-specific cores.}
On \texttt{amd64} the optimized implementation selects an AVX-512 or AVX2 core
once at startup from the \texttt{AVX512VL} CPUID feature bit. On \texttt{arm64}
the optimized implementation uses NEON with the Armv8.2 SHA-3 extension
(\texttt{FEAT\_SHA3}, available on Apple Silicon and Neoverse V1/V2 and N2).
Both architecture-specific paths provide a single-duplex core and batched leaf
kernels; the assembly stays below the mode boundary, so framing, domain
separation, padding, and tree bookkeeping remain shared with the reference path.

\paragraph{Constant time.}
The scalar reference and all three vectorized implementations are constant time
with respect to all inputs. The permutation and the XOR-based absorb/squeeze
contain no secret-dependent branches and no secret-dependent memory or vector
indices. The only indexed table is the round-constant array, addressed by the
public round number; batched loads, stores, gathers, scatters, and
inactive-lane handling are all controlled by public chunk counts and fixed
chunk strides. \Cref{app:kernels} records the architecture-specific addressing
details.

\subsection{Benchmark Methodology}
\label{sec:bench-method}

We measure on two hosts, one per architecture. The \texttt{amd64} host is a
Google Compute Engine \texttt{c4-standard-4} instance with an Intel Xeon Platinum
8581C (Emerald Rapids, $2.30$\,GHz base, AVX-512 including \texttt{AVX512VL},
\texttt{AVX512\_VBMI2}, \texttt{GFNI}, and \texttt{VAES}), two physical cores
with simultaneous multithreading enabled, $48$\,KiB L1d and $32$\,KiB L1i per
core, $2$\,MiB L2 per core, and a $260$\,MiB shared L3, running Debian~12 (kernel
6.1) under KVM. The guest does not expose a \texttt{cpufreq} interface, so the
frequency governor and turbo state are not under our control; we mitigate the
resulting variance statistically (below). The \texttt{arm64} host is an Apple M4
Pro ($10$ performance cores and $4$ efficiency cores; per performance core,
$128$\,KiB L1i, $64$\,KiB L1d, and a $16$\,MiB shared L2) running macOS~26.5.1
(Darwin~25.5), with \texttt{FEAT\_SHA3} present. macOS exposes no userspace
frequency control.

Measurements are collected by a standalone harness (\texttt{cmd/cpb}) that locks
its goroutine to an OS thread and, for each algorithm, operation, and message
length, first calibrates an iteration count that fills at least $100$\,ms, then
records $100$ samples, from which it reports the median cycles per byte and
median wall-clock throughput together with the interquartile range as a
dispersion measure (\Cref{tab:dispersion}). Both metrics are read from the same timed loop, so the
cycles-per-byte and throughput figures for a given measurement come from one
interleaved run rather than two separately scheduled ones. Each sample reuses the
same source and destination buffers, so the reported figures are warm-cache,
steady-state rates. The single-threaded measurement leaves the SMT sibling of the
\texttt{amd64} host idle. We report a sweep of seven message lengths from $1$\,B
to $16$\,MiB.

The cycle counters differ by architecture, and this affects how the
cycles-per-byte figures may be read. On \texttt{amd64} the harness reads
\texttt{RDTSC}; on this part the time-stamp counter is invariant and ticks at the
$2.30$\,GHz reference frequency, so the reported figures are \emph{reference}
cycles per byte and are unaffected by turbo (and convert directly to wall-clock
time). On \texttt{arm64} the harness reads \texttt{CNTVCT\_EL0} and scales it by
the ratio of the peak core frequency to \texttt{CNTFRQ\_EL0}; since Apple exposes
no frequency API, the peak is auto-detected by timing a dependent integer-add
chain and taking the top observed P-state, yielding \emph{core} cycles per byte.
Consequently the cycles-per-byte figures are comparable within an architecture
and against the same-host AES-128-GCM baseline, but not directly across
architectures; absolute throughput (\Cref{tab:throughput}) is the cross-platform
metric.

The baseline is Go's AES-128-GCM implementation
(\texttt{crypto/\allowbreak aes} with \texttt{crypto/\allowbreak cipher}).
It uses AES-NI and \texttt{PCLMULQDQ} on \texttt{amd64}, and the AES
and \texttt{PMULL} instructions on \texttt{arm64}.
Each timed AES-128-GCM call constructs its cipher, so its measurement includes
the key schedule and the GHASH key-power precomputation; this mirrors the
\TW{} measurement, whose one-shot seal and open perform the root duplex
initialization (one permutation) inside the timed call. Both directions are
measured for each scheme; the two directions track each other to within a few
percent across the sweep, with a worst-case divergence of $8\%$ (\TW{} on
\texttt{arm64} at $64$\,B).

\subsection{Throughput}
\label{sec:throughput}

\Cref{tab:cpb} reports cycles per byte across the message-length sweep and
\Cref{tab:throughput} the corresponding wall-clock throughput in the bulk
regime. The dominant feature of the \TW{} rows is the descent produced by the
tree-parallel leaf core: the per-byte cost falls as a message lengthens and its
chunks occupy more SIMD lanes. A message of at most one chunk has no complete
leaf chunk for chunk~$0$ to share a kernel with, so it runs entirely on the
single-duplex core, and the $8$\,KiB column sits at that core's rate. Past one
chunk, chunk~$0$ fusion (\Cref{sec:impl}) keeps every complete chunk on the
batched kernels, and the descent tracks lane occupancy: at $32$\,KiB, chunk~$0$
and three complete leaves run four-wide in the \texttt{amd64} remainder kernels
and as two full pairs on \texttt{arm64}, and $64$\,KiB is the first length
whose eight complete chunks ($8\beta \approx 64$\,KiB) fill the eight-way
($\times 8$) core. On the \texttt{amd64} AVX-512 path \TW{} encryption falls
$1.89 \to 0.78 \to 0.40$ across the $8$, $32$, and $64$\,KiB columns and is
already at its bulk rate at $64$\,KiB, holding at $0.39$--$0.40$ through
$16$\,MiB. The AVX2 path follows the same shape at lower throughput ($2.20 \to
1.10$ over the same span, thereafter between $1.02$ and $1.08$); it runs the
eight instances as two groups of four rather than in a single $8$-wide
register, leaving the AVX-512 core about $2.7\times$ faster in bulk. The
\texttt{arm64} curve flattens earliest ($1.95 \to 0.91 \to 0.88 \to 0.88 \to
0.89$ cycles per byte from $8$\,KiB to $16$\,MiB): the eight-way core itself
processes its batch as four two-instance pairs, so the fused $2$-wide kernel
runs at essentially the same per-chunk rate, and a $32$\,KiB message---chunk~$0$
and three leaves as two full pairs---is already within $3\%$ of the $16$\,MiB
floor. In wall-clock terms \TW{} reaches $5.77$\,GB/s on the \texttt{amd64}
AVX-512 host and $5.04$\,GB/s on the M4 Pro for $16$\,MiB messages.

\begin{table}
\centering
\caption{Median cycles per byte ($100$ samples). The \texttt{amd64} figures are
\texttt{RDTSC} reference cycles at the $2.30$\,GHz invariant time-stamp counter;
the \texttt{arm64} figures are core cycles at the auto-detected peak performance-core
frequency. Cycle counts are not directly comparable across architectures
(\Cref{sec:bench-method}).}
\label{tab:cpb}
\begin{tabular}{l rrrrrrr}
\toprule
& \multicolumn{7}{c}{Message length} \\
\cmidrule(l){2-8}
& $1$\,B & $64$\,B & $8$\,KiB & $32$\,KiB & $64$\,KiB & $1$\,MiB & $16$\,MiB \\
\midrule
\multicolumn{8}{l}{\emph{Intel Xeon 8581C (Emerald Rapids), AVX-512}} \\
\quad \TW{} encrypt      & 590 & 9.27 & 1.89 & 0.78 & 0.40 & 0.39 & 0.40 \\
\quad \TW{} decrypt      & 615 & 9.72 & 1.90 & 0.75 & 0.40 & 0.39 & 0.39 \\
\quad AES-128-GCM seal   & 765 & 13.23 & 0.38 & 0.32 & 0.30 & 0.30 & 0.30 \\
\quad AES-128-GCM open   & 785 & 12.79 & 0.37 & 0.31 & 0.30 & 0.29 & 0.29 \\
\midrule
\multicolumn{8}{l}{\emph{Intel Xeon 8581C (Emerald Rapids), AVX2}} \\
\quad \TW{} encrypt      & 656 & 10.31 & 2.20 & 1.10 & 1.02 & 1.07 & 1.08 \\
\quad \TW{} decrypt      & 683 & 10.70 & 2.21 & 1.11 & 1.08 & 1.07 & 1.08 \\
\midrule
\multicolumn{8}{l}{\emph{Apple M4 Pro, NEON\,+\,\texttt{FEAT\_SHA3}}} \\
\quad \TW{} encrypt      & 620 & 9.77 & 1.95 & 0.91 & 0.88 & 0.88 & 0.89 \\
\quad \TW{} decrypt      & 667 & 10.59 & 2.00 & 0.89 & 0.87 & 0.87 & 0.87 \\
\quad AES-128-GCM seal   & 1044 & 17.28 & 0.54 & 0.45 & 0.44 & 0.43 & 0.44 \\
\quad AES-128-GCM open   & 1055 & 17.31 & 0.52 & 0.43 & 0.42 & 0.41 & 0.42 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Measured wall-clock throughput (GB/s, $\mathrm{GB} = 10^9$ bytes) from
the same \texttt{cmd/cpb} run as \Cref{tab:cpb}, encryption direction; the
decryption direction tracks it. The \texttt{amd64} AES-128-GCM row is the AVX-512
host and is unaffected by the \TW{} core selection.}
\label{tab:throughput}
\begin{tabular}{l rrrrr}
\toprule
& $8$\,KiB & $32$\,KiB & $64$\,KiB & $1$\,MiB & $16$\,MiB \\
\midrule
\multicolumn{6}{l}{\emph{Intel Xeon 8581C (Emerald Rapids)}} \\
\quad \TW{} (AVX-512)  & 1.22 & 2.95 & 5.78 & 5.94 & 5.77 \\
\quad \TW{} (AVX2)     & 1.05 & 2.09 & 2.25 & 2.15 & 2.14 \\
\quad AES-128-GCM      & 6.11 & 7.27 & 7.57 & 7.68 & 7.63 \\
\midrule
\multicolumn{6}{l}{\emph{Apple M4 Pro}} \\
\quad \TW{} (NEON+SHA3) & 2.30 & 4.92 & 5.06 & 5.10 & 5.04 \\
\quad AES-128-GCM       & 8.25 & 9.89 & 10.18 & 10.33 & 10.09 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Dispersion.}
Each cell of \Cref{tab:cpb,tab:throughput} is the median of $100$ samples;
\Cref{tab:dispersion} summarizes their spread as the interquartile range
(IQR) relative to the median. The medians are stable: across the sweep the
relative IQR of the \TW{} cycles-per-byte measurements is at most $1.6\%$
on the \texttt{amd64} AVX-512 path, $2.1\%$ on AVX2, and $1.0\%$ on the M4
Pro, with per-path medians of $1.2\%$, $1.4\%$, and $0.6\%$. The full
min--max range is wider on the \texttt{amd64} guest---up to $16.5\%$
(AVX-512) and $20.2\%$ (AVX2) at isolated lengths---because its turbo and
governor states are not under our control (\Cref{sec:bench-method}); these
are tail excursions that the IQR excludes, and the M4 Pro, whose frequency
is steadier, keeps even its full range within $4.7\%$. We therefore report
medians throughout and treat the IQR as the dispersion measure.

\begin{table}
\centering
\caption{Cycles-per-byte measurement dispersion for \TW{} across the
seven-length sweep (seal and open, $100$ samples per point), as the
interquartile range relative to the median. The final column is the widest
single-point min--max range; its size on the \texttt{amd64} guest reflects
the turbo and governor states we cannot pin (\Cref{sec:bench-method}) and
is excluded from the IQR as a tail effect.}
\label{tab:dispersion}
\begin{tabular}{l rrr}
\toprule
& \multicolumn{2}{c}{Relative IQR} & Max \\
\cmidrule(lr){2-3}
Path & median & max & range \\
\midrule
Xeon 8581C, AVX-512 & $1.2\%$ & $1.6\%$ & $16.5\%$ \\
Xeon 8581C, AVX2    & $1.4\%$ & $2.1\%$ & $20.2\%$ \\
Apple M4 Pro        & $0.6\%$ & $1.0\%$ & $\phantom{0}4.7\%$ \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Latency}
\label{sec:latency}

For short messages the cost is set by the serial root duplex and is independent
of the parallel leaf machinery. A message of at most $\rho = 167$ bytes occupies
a single rate block and never enters leaf mode, so it costs exactly two
permutations---one to initialize the root duplex and one to close the message
block and extract the tag. The $1$\,B and $64$\,B columns of \Cref{tab:cpb} bear
this out: per-message latency is nearly flat across them at roughly $590$
reference cycles on \texttt{amd64} ($590$ at $1$\,B versus $9.27 \times 64
\approx 593$ at $64$\,B) and $620$ core cycles on \texttt{arm64} ($620$ versus
$9.77 \times 64 \approx 625$), i.e.\ about $295$ and $310$ cycles per
\Keccakp{} respectively. Because such messages bypass the leaf
core entirely, leaf-level parallelism imposes no latency penalty on them.

The latency/throughput trade-off appears instead in the intermediate regime,
which chunk~$0$ fusion has narrowed to roughly the one-to-eight-chunk band. The
worst per-byte cost in the sweep is the single-chunk regime at $8$\,KiB
($1.9$--$2.2$ cycles per byte across the three paths), where the message is the
chunk-$0$ phase alone on the single-duplex core. Once the message has complete
leaf chunks for chunk~$0$ to share a kernel with, the cost falls quickly: by
$32$\,KiB \TW{} is within a factor of two of its AVX-512 floor and within $3\%$
of its \texttt{arm64} floor, and the floor itself is reached once the eight-way
core fills at $64$\,KiB. The root duplex also bounds the tail of a long
message: the final tag cannot be produced until chunk~$0$ has been processed and
every leaf tag has been absorbed into the aggregation transcript. That absorption
is cheap---each rate block of the root absorbs five $32$-byte leaf tags, so a
$16$\,MiB message ($\approx 2000$ leaves) adds on the order of $400$ root
permutations against roughly $10^5$ permutations of leaf work, under $0.5\%$
overhead---so the serial root does not materially cap bulk throughput.

\subsection{Comparison with Other AEADs}
\label{sec:compare-perf}

We compare against the one baseline measured under the same harness on the same
hosts, the Go standard library's hardware-accelerated AES-128-GCM
(\Cref{tab:cpb,tab:throughput}). The harness times \TW{} and AES-128-GCM
back-to-back at each length and reads both metrics from the same loop, so the
cycles-per-byte and throughput comparisons hold under identical conditions and
agree. In the bulk regime AES-128-GCM is faster on both architectures, as
expected for a primitive with dedicated AES and carryless-multiply instructions:
at $16$\,MiB it runs at $0.30$ cycles per byte on \texttt{amd64} and $0.44$ on
\texttt{arm64}, against $0.40$ and $0.89$ for \TW{}---about $1.3\times$ and
$2\times$ faster. The wall-clock throughputs show the same margins: \TW{} reaches
$5.77$ and $5.04$\,GB/s against AES-128-GCM's $7.63$ and $10.09$\,GB/s. The wider
\texttt{arm64} gap reflects the strength of Apple's AES and \texttt{PMULL} units.
\TW{} attains these rates with a permutation that has no dedicated hardware
support, relying only on the SHA-3 extension on \texttt{arm64} and on general SIMD
on \texttt{amd64}.

The ordering reverses for very short messages, where AES-128-GCM's key schedule
and GHASH key-power precomputation dominate: at $1$\,B AES-128-GCM costs $765$
and $1044$ cycles on the two hosts against \TW{}'s $590$ and $620$. This
comparison is setup-bound rather than representative of steady state, since each
timed call rebuilds its cipher; it nonetheless reflects the per-message cost an
application pays when it does not amortize key setup across messages. In the
sub-bulk regime AES-128-GCM is several times faster at one chunk ($0.38$ versus
$1.89$ cycles per byte at $8$\,KiB on \texttt{amd64}), but the gap narrows
quickly once the fused kernels engage: about $2.4\times$ at $32$\,KiB, and the
bulk ratio from $64$\,KiB on. \TW{}'s intended value relative to AES-128-GCM
lies in the tree structure and committing security properties analyzed in
\Cref{sec:aead-security,sec:root-tag-hash-security} rather than in raw speed.
