\section{Conclusion}
\label{sec:conclusion}

\TW{} is a nonce-based AEAD mode built as a two-level tree of keyed duplexes over
a single \Keccakp{} permutation. Its chunk decomposition is canonical, while the
number of leaf duplexes evaluated in parallel is an implementation choice rather
than a mode parameter. This gives scalar, SIMD, and multicore implementations the
same ciphertexts and tags, with constant working memory and scalable
parallelism.

The central security claim is that the authentication tag behaves like a
digest-like commitment to the full $(K, N, A, M)$ context. In the public
permutation model, via an intermediate random oracle and the flat sponge lift, we
prove concrete multi-user indistinguishability and derive all-in-one AE as its
single-user corollary. We also prove collision, second-preimage, and preimage
security for the root tag wrapper. Those hash-style guarantees yield the
AEAD-facing commitment results, including full-input \textsf{CMTDs-4} security
and context discoverability ($\mathsf{CDY}^\ast$), at a $128$-bit target for the
implemented parameters.

The implementation results show that this commitment is not purchased by giving
up the performance profile of modern duplex AEADs. Vectorized \texttt{amd64} and
\texttt{arm64} implementations exploit the scalable leaf structure, exceed
$10$\,Gbit/s, and reach $50$--$75\%$ of hardware-accelerated AES-128-GCM
throughput.

Several questions remain open (\Cref{sec:limitations}): a nonce-misuse-resistant
variant, security under release of unverified plaintext, and sharper bounds,
whether through a keyed duplex treatment of the BDPV11-style phasing used here or
through a beyond-birthday argument. More broadly, \TW{} adds to the evidence that
a single, well-scrutinized \Keccak{} permutation can support authenticated
encryption that is fast, scalable, and committing.
