\section{Vectorized Kernel Details}
\label{app:kernels}

This appendix details the optimized cores summarized in \Cref{sec:impl}:
their shared batching structure, chunk~$0$ fusion, instruction selection,
register layout, remainder handling, and constant-time addressing.

The optimized paths share the same logical decomposition but differ in their
batch widths, remainder strategy, and state writeback points:
\begin{center}
\small
\begin{tabular}{@{}p{0.22\linewidth} p{0.72\linewidth}@{}}
\toprule
Path & Cores and writeback \\
\midrule
\texttt{amd64} AVX-512 &
Wide: one eight-state ZMM group. Remainder: masked $2$--$7$ state AVX-512 core.
Single duplex: AVX-512 permutation. Chunk~$0$: all active states are written
back through \texttt{state8}. \\
\texttt{amd64} AVX2 &
Wide: two four-state YMM groups. Remainder: $2$--$7$ states with dummy inactive
lanes. Single duplex: general purpose register permutation. Chunk~$0$: all
active states are written back through \texttt{state8}. \\
\texttt{arm64} NEON+SHA3 &
Wide: four two-state NEON pairs. Remainder: two-state pair core. Single duplex:
NEON/SHA-3 permutation. Chunk~$0$: pair $(0,1)$ is written back in the wide
core, and both states are written back in the pair core. \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Shared batching structure.}
The implementation separates the sequential root duplex from the independent
leaf duplexes. The root duplex normally uses a single-duplex ($\times 1$)
core, while complete leaf chunks are grouped into eight-instance batches.
Every complete leaf chunk is exactly $\beta = 49\rho$ bytes, so all eight
instances in a batch follow the same sequence of $49$ full $\rho$-blocks:
the first $48$ close with \textsc{msg\_more}, and the last closes with
\textsc{msg\_last}. A single public block index therefore drives the whole
batch. The batched state is lane-major: for each of the $25$ Keccak lanes,
the kernel stores the corresponding 64-bit word of each active instance
together in vector registers. Equivalently, for Keccak lane $i$ the vector
register holds $(S_0[i],\ldots,S_7[i])$ across the active duplex states, so
one vector operation updates the same lane in several states.

\paragraph{Chunk~$0$ fusion.}
Chunk~$0$ is part of the root transcript, but its message phase has the
same kernel-visible block schedule as a complete leaf chunk. The optimized
paths exploit this by placing the post-AD root state into lane~$0$ of the
first batched call and placing the first leaf chunks in the remaining lanes.
When the message has at least seven complete leaf chunks, this fused call
uses the $\times 8$ core; below that, it uses the same remainder machinery
that drains incomplete batches. The output state from lane~$0$ is written
back to the root duplex, which then absorbs the leaf tags produced by the
same call.

\paragraph{Remainder and tail handling.}
Messages are otherwise decomposed into full eight-chunk batches plus a
remainder. On \texttt{amd64}, a register-resident remainder kernel handles
two to seven complete chunks in one call, reading each active chunk in
place; on \texttt{arm64}, a $2$-wide kernel drains the remainder two chunks
at a time. A single leftover complete chunk, a partial trailing chunk, and
the count-aggregation tail use the single-duplex core. The \texttt{amd64}
assembly chunk kernels handle the $48$ full \textsc{msg\_more} blocks and
leave the final \textsc{msg\_last} block plus leaf tag extraction to shared
Go code, keeping byte-granular tail logic out of assembly. The
\texttt{arm64} batched kernels process the complete chunk and store back the
states needed for chunk~$0$ fusion: pair $(0,1)$ in the $\times 8$ kernel,
and both active states in the $2$-wide kernel.

\paragraph{\texttt{amd64}.}
The \texttt{amd64} implementation provides AVX-512 and AVX2 cores and selects
between them once at startup from an AVX-512 feature probe requiring OS support
for YMM/ZMM state, \texttt{AVX512F}, and \texttt{AVX512VL}. The single-duplex
permutation has two variants: a general-purpose-register core adapted from the
standard library's \Keccak{} permutation (using the lane-complement trick so
that $\chi$ requires no separate negation), and an AVX-512 variant; the root
duplex uses whichever matches the selected core.

The eight-way AVX-512 core packs the lane-major state into 25 ZMM registers,
one per lane with all eight instances in the register's eight 64-bit slots, and
performs the permutation with no cross-lane shuffles: rotations use
\texttt{VPROLQ}, and \texttt{VPTERNLOGQ} fuses the $\theta$ $D$-term formation
and the $\chi$ \mbox{and-not} into single three-input logic instructions. The
fused chunk kernel reads the eight chunks with contiguous loads, transposes each
rate block into the lane-major layout in registers
(\texttt{VPUNPCKLQDQ}/\texttt{VPUNPCKHQDQ} and \texttt{VSHUFI64X2}), absorbs on
the lane-major state, and transposes each output block back for a contiguous
store. Since $\rho = 167 = 20 \cdot 8 + 7$, the first $20$ rate lanes use this
transposed path and only the trailing $7$ bytes in lane~$20$ use a masked
gather. These sequential accesses are prefetcher-friendly, whereas per-lane
gathers and scatters at the chunk stride $\beta$
(\texttt{VPGATHERQQ}/\texttt{VPSCATTERQQ}) would stall on cold memory and cap
the long-message rate.

The register-resident kernel that drains a two-to-seven-chunk AVX-512 remainder
instead uses that per-lane gather/scatter form under a mask, reading the active
chunks in place: the transpose's shuffle work is constant regardless of the
chunk count and would be spent partly on inactive lanes, whereas the gathers
scale with the active element count.

The eight-way AVX2 core, lacking 512-bit registers, runs the eight instances as
two groups of four (four 64-bit lanes per YMM register), rotating by shift-or
and computing $\chi$ with \texttt{VPANDN}. The AVX2 path drains remainders with
a variant of the grouped-by-four kernels that aims each inactive instance's
loads and stores at a dummy block inside the kernel frame with a zero advance
stride, so inactive instances touch no memory beyond the remainder and the hot
loop stays branch-free.

\paragraph{\texttt{arm64}.}
The \texttt{arm64} path uses NEON plus the Armv8.2 SHA-3 extension
(\texttt{FEAT\_SHA3}), available on Apple Silicon and on Neoverse V1/V2 and N2.
The permutation is expressed with the extension's fused instructions:
\texttt{EOR3} (three-input XOR) for the $\theta$ column parities, \texttt{RAX1}
(rotate-by-one and XOR) for the $\theta$ $D$-terms, \texttt{XAR} (XOR then
rotate) to fuse the $\theta$ accumulation with the $\rho$ rotation, and
\texttt{BCAX} (bit-clear and XOR) for $\chi$. The single-duplex core stores
each Keccak lane in one 64-bit \texttt{D} lane across the 25 vector registers.
The eight-way core packs two instances per 128-bit register and processes the
batch of eight as four such pairs, using \texttt{ZIP1} and duplicating moves to
interleave and extract the two instances of each lane in the fused chunk kernel.
The same pair machinery backs a $2$-wide kernel that drains a leaf-chunk
remainder two chunks at a time---one instance per $64$-bit half of a $128$-bit
register---at roughly twice the single-duplex per-chunk rate. Both batched
kernels store the permutation state back into the batch after the closing
block---the $\times 8$ kernel for its first pair, the $2$-wide kernel for both
instances---which is the writeback that permits the root duplex to occupy
lane~$0$.

\paragraph{Constant-time addressing.}
The optimized kernels contain no secret-dependent branches and no
secret-dependent memory or vector indices. The only indexed table is the
round-constant array, addressed by the public round number. The AVX-512
steady-state transpose uses contiguous loads and stores; the remaining
gathers and scatters, for the partial rate lane and register-resident
remainder kernel, use fixed public chunk strides under masks determined by
the public chunk count. The AVX2 remainder kernel redirects inactive
instances to a dummy block in its stack frame with a zero advance stride,
again selected only by the public chunk count. The \texttt{arm64} pair
kernels use fixed lane interleaving and extraction patterns. None of these
addresses depends on the key, nonce, plaintext, or decrypted plaintext.
