\section{Committing-Notion Bounds}
\label{app:committing-transfer}

This appendix establishes the committing-security bounds beyond the
random-oracle CMTDs-3 theorem of
\Cref{thm:cmtds3-ro}. The D-notions reduce to
CMTDs-3 by success-preserving forwarding. The
E-notions are bounded directly by the same final-root candidate-collision
argument, with the challenger encryption checks counted as construction
work in $N$.

\begin{lemma}[Forwarding Reductions]
\label{lem:cmtds-identity-reductions}
Fix $s \geq 2$. Let $X$ be either $\mathsf{CMTDs\text{-}3}$ or
$\mathsf{CMTDs\text{-}4}$. For every
$s$-way $X$-adversary $\mathcal{A}$ against \TW{}, the forwarding
reduction $\mathcal{A}^*=\mathcal{A}$ is an $s$-way
CMTDs-3 adversary satisfying
\begin{align*}
  \Adv^X_\TW(\mathcal{A}) &\leq \Advcmtds{3}_\TW(\mathcal{A}^*), \\
  \Nprim(\mathcal{A}^*) &= \Nprim(\mathcal{A}), \\
  \Ntot(\mathcal{A}^*) &\leq \Ntot(\mathcal{A}).
\end{align*}
\end{lemma}

\begin{proof}
The CMTDs-3 case is the identity game. A
CMTDs-4 winner is also a
CMTDs-3 winner. Indeed, if a winning transcript had
$(K_i,N_i,A_i)=(K_j,N_j,A_j)$ for some $i \neq j$, determinism of
$\Dec$ would give
$M_i=\Dec_{K_i}(N_i,A_i,C \concat T)=M_j$, contradicting the
pairwise distinctness of the full tuples
$(K_i,N_i,A_i,M_i)$. Thus a CMTDs-4 winner also has
pairwise distinct triples and is a CMTDs-3 winner on
the same output. The forwarding reduction performs no additional
primitive-interface queries. In the CMTDs-4 case, if
the target CMTDs-3 game reaches its deterministic
decryption checks, the source CMTDs-4 game also
reaches deterministic decryption checks on the same ciphertext and
tuples; otherwise the target contributes no construction work. Hence
the target construction cost is at most the source construction cost.
\end{proof}

\begin{lemma}[CMTDs-1 Key-Precheck Reduction]
\label{lem:cmtds1-precheck-reduction}
Fix $s \geq 2$. For every $s$-way CMTDs-1 adversary
$\mathcal{A}$ against \TW{}, define $\mathcal{A}^*$ as follows. It runs
$\mathcal{A}$ to obtain $C \concat T$ and tuples
$(K_i,N_i,A_i,M_i)_{i=1}^s$. If the tuples fail the
CMTDs-1 syntax, length, or pairwise-$\WiC_1$ checks,
then $\mathcal{A}^*$ outputs a fixed losing
CMTDs-3 instance rejected before any decryption
check. Otherwise, it forwards the same
$(C \concat T,(K_i,N_i,A_i,M_i)_{i=1}^s)$ to the
CMTDs-3 challenger. Then
\begin{align*}
  \Advcmtds{1}_\TW(\mathcal{A})
    &\leq \Advcmtds{3}_\TW(\mathcal{A}^*), \\
  \Nprim(\mathcal{A}^*) &= \Nprim(\mathcal{A}), \\
  \Ntot(\mathcal{A}^*) &\leq \Ntot(\mathcal{A}).
\end{align*}
\end{lemma}

\begin{proof}
The syntax and pairwise-$\WiC_1$ prechecks are source-game rejection
checks, and the eager length precheck is success preserving because
\TW{} decryption returns either $\bot$ or a message of length $\|C\|$.
Thus no winning CMTDs-1 transcript is discarded. On
the forwarding branch, pairwise $\WiC_1$-distinctness means the keys
$K_i$ are pairwise distinct, hence the triples $(K_i,N_i,A_i)$ are
pairwise distinct. Thus every source winner forwarded by
$\mathcal{A}^*$ satisfies the target CMTDs-3 syntax,
length, and triple-distinctness checks, and the target decryption
checks are the same deterministic checks as in the source game.

The reduction performs no additional primitive-interface queries. On the
fixed-losing branch, both the source game and target reduction reject
before construction work. On the forwarding branch, the target
decryption checks coincide with the source decryption checks. Therefore
the target construction cost is at most the source construction cost.
\end{proof}

\begin{lemma}[Random-Oracle CMTs]
\label{lem:cmts-ro}
Fix $s \geq 2$ and $\ell \in \{1,3,4\}$. For every $s$-way
CMTs-$\ell$ adversary $\mathcal{B}$ in the \TW{}
random-oracle model,
\[
  \Advcmts{\ell}_{\RO}(\mathcal{B})
  \;\leq\; \RootColl_{\tauroot}(\qRO(\mathcal{B}), s)
  =
  \frac{\binom{\qRO(\mathcal{B}) + s}{s}}{2^{\tauroot(s - 1)}}.
\]
\end{lemma}

\begin{proof}
Run the random-oracle CMTs-$\ell$ game: after
$\mathcal{B}$'s direct $\ROflat$ queries, the challenger checks syntax
and pairwise $\WiC_\ell$-distinctness of the submitted tuples
$(K_i,N_i,A_i,M_i)_{i=1}^s$, computes
\[
  C_i \concat T_i = \Enc_{K_i}^{\RO}(N_i,A_i,M_i),
\]
and accepts iff all $C_i \concat T_i$ are equal.

Build the same candidate sequence as in \Cref{thm:cmtds3-ro}. During
$\mathcal{B}$'s direct oracle phase, append every distinct direct-query
input whose decoded class is a root tag output-point class --- $\Rmsg^+$
(the single-chunk root tag, with the aggregation phase elided when
$n = 0$) or $\Rtag$ (the multi-chunk root tag) --- immediately before
the corresponding direct $\ROflat$ lookup first samples that input. This
predicate depends on the queried input alone through the exact decoder
of \Cref{lem:bridge-decode}, and by \Cref{cor:output-sep} each input
decodes to at most one output-point class. Since there is no
construction oracle before $\mathcal{B}$ outputs its tuples, these
candidates are first touched at their append steps.

After the tuple output, stop appending challenger candidates if the
syntax or pairwise-$\WiC_\ell$ check fails. Otherwise, as the challenger
computes the $s$ deterministic encryption checks, let $R_i$ be the final
root transcript reached by the $i$-th encryption and append
$\flatmap(R_i)$ immediately before the root tag oracle answer is sampled,
unless that input is already in the sequence. If such an input was
already touched by a direct query, then \Cref{lem:bridge-decode} and
\Cref{cor:output-sep} imply that the earlier query was a final-root
candidate. Earlier challenger lookups outside the final-root class are
separated by \Cref{cor:output-sep}. An earlier challenger final-root
lookup with a different address does not affect the new candidate. An
earlier challenger final-root lookup with the same address is either a
root tag answer sampling, in which case the address was already
appended and is not appended again, or the chunk-$0$-closing
\sigmsglast{} call of an $n \geq 1$ encryption check that reaches the
same $\Rmsg^+$ address (possible only for $\ell = 4$, where two checks
may share $(K, N, A)$ and the chunk-$0$ ciphertext); that call requests
zero output bits and continues into its aggregation phase, so it does
not sample the lazy-table value at the address. In all cases the
lazy-table value of each newly appended challenger candidate is first
sampled at its append step, as \Cref{lem:adaptive-candidate-collision}
requires, and the sequence length is at most $\qRO(\mathcal{B})+s$.

On a winning execution, the accepted encryptions are all equal. Hence
their ciphertext-body lengths are equal. Pairwise triple distinctness
follows from the winning predicates: for $\ell \in \{1,3\}$ it follows
directly from pairwise $\WiC_\ell$-distinctness, and for $\ell=4$ equal
triples would force the equal encryption value to decrypt, by correctness
and determinism, to a single message $M_i = M_j$, so the full tuples
$(K_i,N_i,A_i,M_i)$ and $(K_j,N_j,A_j,M_j)$ would coincide, contradicting
pairwise $\WiC_4$-distinctness. Therefore \Cref{cor:triple-sep} makes the
bridged final-root inputs
\[
  \flatmap(R_1),\dots,\flatmap(R_s)
\]
pairwise distinct. Since all encryptions are equal, their root tags are
the same value $T$, so the $\tauroot$-bit projections at these $s$
distinct final-root candidates are all equal to $T$. The win event is
contained in the $s$-way candidate-collision event, and
\Cref{lem:adaptive-candidate-collision} with $Q=\qRO(\mathcal{B})$ and
$\tau=\tauroot$ gives the claim.
\end{proof}

\begin{corollary}[Public-Permutation CMTs]
\label{cor:cmts-pp}
Fix $s \geq 2$ and $\ell \in \{1,3,4\}$. For every $s$-way
CMTs-$\ell$ adversary $\mathcal{A}$ against \TW{} with
$\Nprim$ direct primitive queries and total cost at most $\Ntot$,
\[
  \Advcmts{\ell}_\TW(\mathcal{A})
  \;\leq\;
  \Lift_c(\Ntot) + \RootColl_{\tauroot}(\Nprim, s).
\]
\end{corollary}

\begin{proof}
The CMTs-$\ell$ game is a win-event experiment with no
construction oracle during the adversary's run. Its construction cost
$N$ counts the deterministic encryption checks performed by the
challenger after $\mathcal{A}$ outputs its tuples. By the flat-sponge
lift bound (\Cref{lem:lift-bound}), replacing $(\pi,\pi^{-1})$ by
$(\Sim^{\ROflat},\Sim^{-1,\ROflat})$ and the challenger encryption
checks by their random-oracle counterparts costs at most
$\Lift_c(\Ntot)$. Let
$\mathcal{B}_{\mathrm{derived}} =
\mathcal{B}_{\mathrm{derived}}(\mathcal{A})$ be the adversary of
\Cref{lem:derived-adversary}. The derived-adversary construction gives
\[
  \Advcmts{\ell}_\TW(\mathcal{A})
  \leq \Lift_c(\Ntot)
    + \Advcmts{\ell}_{\RO}(\mathcal{B}_{\mathrm{derived}}),
\]
with $\qRO(\mathcal{B}_{\mathrm{derived}}) \leq \Nprim$. Apply
\Cref{lem:cmts-ro} and use monotonicity of
$\RootColl_{\tauroot}(\cdot,s)$.
\end{proof}

\paragraph{Combined bound.}
Combining the D-notion forwarding lemmas above with
\Cref{cor:cmtds3-pp}, and the E-notion bound of \Cref{cor:cmts-pp}, gives
the same root-collision envelope for all six committing notions of \cite{BH22}: for every
\[
  X \in \bigl\{\mathsf{CMTDs\text{-}1},\, \mathsf{CMTDs\text{-}3},\,
              \mathsf{CMTDs\text{-}4},\, \mathsf{CMTs\text{-}1},\,
              \mathsf{CMTs\text{-}3},\, \mathsf{CMTs\text{-}4}\bigr\}
\]
and every $s$-way $X$-adversary $\mathcal{A}$ against \TW{},
\[
  \Adv^X_\TW(\mathcal{A})
  \;\leq\;
  \Lift_c(\Ntot(\mathcal{A}))
  + \frac{\binom{\Nprim(\mathcal{A}) + s}{s}}{2^{\tauroot(s-1)}}.
\]
For the D-notions, the forwarding or key-precheck reduction performs no
additional primitive-interface queries and no additional construction
work beyond the source-game decryption checks, so
$\Nprim(\mathcal{A}^*) = \Nprim(\mathcal{A})$ and
$\Ntot(\mathcal{A}^*) \leq \Ntot(\mathcal{A})$; the latter enters the
displayed $\Lift_c$ term through the monotonicity of $\Lift_c$ in its
argument. For the E-notions, no
reduction is used: the challenger encryption checks are the source-game
construction work already counted in $N$ by \Cref{sec:resources}.
