\documentclass[journal=tosc,submission,notanonymous]{iacrtrans}

\input{preamble}
\input{macros}

\title[TW128]{TW128: A Tree-Structured Duplex Authenticated Encryption Mode}
\author{Coda Hale}
\institute{Hale Institute for Bicycle Appreciation}

\begin{document}

\maketitle

\keywords{authenticated encryption \and committing security \and sponge constructions \and duplex constructions \and Keccak}

\begin{abstract}
  AEAD tags are often expected to be compact commitments to the full encryption
  context, an intuition reinforced by common experience with hash-based MACs
  such as HMAC. The AEAD literature has only recently begun to formalize this
  expectation through notions such as committing security and encryptment, but
  standard deployed modes such as AES-GCM and ChaCha20-Poly1305 do not provide
  it. We present \TW{}, a nonce-based
  authenticated encryption mode with associated data that adapts the
  KangarooTwelve tree-hashing pattern to keyed duplex encryption over
  \Keccakp{}. A serial root duplex binds the key, nonce, and associated data,
  encrypts the first message chunk, and aggregates tags from independently keyed
  leaf duplexes for the remaining chunks. The leaf decomposition is canonical,
  but the number of leaves evaluated at once is an implementation choice:
  scalar, SIMD, and multicore implementations produce identical ciphertexts and
  tags without making the degree of parallelism a mode parameter.

  The final root tag is the authentication tag and is also analyzed as a
  digest-like commitment to the full $(K, U, A, M)$ context. In the public
  permutation model, via an intermediate random oracle and the flat sponge lift,
  we prove concrete multi-user indistinguishability and derive all-in-one
  authenticated encryption as the single-user corollary. We also prove
  integrity under release of unverified plaintext in the sense of
  \cite{ABLMMY14}. Separately, we prove that the wrapper returning the tag is a
  secure hash of the full context---collision-, second-preimage-, and
  preimage-resistant in the standard hash-function sense. The same tag analysis
  gives the AEAD-facing committing results, including full-input
  \textsf{CMTDs-4} committing security. At the implemented
  parameters, all stated notions meet a $128$-bit security target. Vectorized
  \texttt{amd64} and \texttt{arm64}
  implementations recover the scalable performance profile of the tree design:
  in bulk they reach up to $48$\,Gbit/s, with the AVX-512 and \texttt{arm64}
  paths delivering $51$--$76\%$ of hardware-accelerated AES-128-GCM
  throughput.
\end{abstract}

\input{sections/01-introduction}
\input{sections/02-preliminaries}
\input{sections/03-tw128}
\input{sections/04-security-model}
\input{sections/05-authenticated-encryption-security}
\input{sections/06-root-tag-hash-security-committing-security}
\input{sections/07-concrete-security-summary}
\input{sections/08-performance}
\input{sections/09-discussion}
\input{sections/10-conclusion}

\section*{Acknowledgments}
A hearty thank-you to my wife, who remains reasonably mystified at my choice
of hobbies.

\bibliographystyle{alpha}
\bibliography{refs}

\appendix
\input{sections/appendix-lemmas}
\input{sections/appendix-flat-sponge-lift}
\input{sections/appendix-kernels}
\input{sections/appendix-test-vectors}

\end{document}
